This notebook follows along with the following video:   

[Exploring Data(part 2) - Extraction & Transformation) ](https://www.youtube.com/watch?v=v11SWrC6qGk&list=PLjPbBibKHH18I0mDb_H4uP3egypHIsvMn&index=10)

Like the previous video we load up our file by using Rcurl instead of like he does in his video. 

First make sure RCurl is installed.

```{r eval=FALSE}
install.packages("RCurl")
```

Then make sure it is loaded:

```{r}
library("RCurl")
```

Bascially Instead of reading from the local computer we will read it from online and then read it in to the data frame as follows

```{r}
textString<-getURL("https://raw.githubusercontent.com/stedy/Machine-Learning-with-R-datasets/master/usedcars.csv")
df<-read.csv(text=textString, stringsAsFactors=FALSE)
```

Next we convert the transmission field in the data to a factor: In the video he mentions having done this. So the code below does this.

```{r}
df$transmission<-factor(df$transmission)
```

So now you can start with the video at [0:42](https://youtu.be/v11SWrC6qGk?list=PLjPbBibKHH18I0mDb_H4uP3egypHIsvMn&t=42)

```{r}
str(df)
```

```{r}
head(df)
```

```{r}
subset(df, color %in% "Yellow")
```

```{r}
subset(df, mileage > 100000)
```

```{r}
subset(df, transmission %in% "MANUAL")
```

```{r}
head(df)
```

```{r}
head(df$color)
```

```{r}
df$color[1]
```

```{r}
df$color[1:3]
```

```{r}
df$color[100]
```

```{r}
table(df$color)
```

```{r}
head(df)
```

```{r}
df[1,]
```

```{r}
df[1,3]
```

```{r}
df[c(1,3,6), 5]
```

```{r}
df[c(1,3,6), "color"]
```

```{r}
df[c(1,3,6), c("color","transmission")]
```

```{r}
df[c(1,3,6), -c(5,6)]
```
