This notebook follows along with the following video:   

[Exploring Data(part 3) - Univariate Summaries ](https://www.youtube.com/watch?v=EVmuPZgTf2U&list=PLjPbBibKHH18I0mDb_H4uP3egypHIsvMn&index=11)

Like the previous video
we load up our file by using Rcurl instead of like he does in his videos. The following code sets this up.

First make sure RCurl is installed.

```{r eval=FALSE}
install.packages("RCurl")
```

Then make sure it is loaded:

```{r}
library("RCurl")
```

Bascially Instead of reading from the local computer we will read it from online and then read it in to the data frame as follows

```{r}
textString<-getURL("https://raw.githubusercontent.com/stedy/Machine-Learning-with-R-datasets/master/usedcars.csv")
df<-read.csv(text=textString, stringsAsFactors=FALSE)
```

Now you can start at [1:40](https://youtu.be/EVmuPZgTf2U?list=PLjPbBibKHH18I0mDb_H4uP3egypHIsvMn&t=100) with the same dataframe as in the video

```{r}
str(df)
```

```{r}
head(df)
```

```{r}
head(df$transmission)
```

```{r}
df$transmission <- factor(df$transmission)
```

```{r}
head(df)
```

```{r}
str(df)
```

```{r}
table(df$transmission)
```

```{r}
length(df$transmission)
```

```{r}
table(df$transmission)/length(df$transmission)
```

```{r}
pie(table(df$transmission))
```

```{r}
barplot(table(df$transmission))
```

```{r}
head(df$mileage)
```

```{r}
mean(df$mileage)
```

```{r}
median(df$mileage)
```

```{r}
var(df$mileage)
```

```{r}
sd(df$mileage)
```

```{r}
range(df$mileage)
```

```{r}
hist(df$mileage)
```

```{r}
boxplot(df$mileage)
```

```{r}
boxplot(df$mileage, horizontal=TRUE)
```
