---
title: "Bakery Sales"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

```{r}
options(repr.plot.width=4, repr.plot.height=4)
options("scipen"=100, "digits"=4)
if(!require("readr")) install.packages("readr")
library("readr")
url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vS3t-anI3_buZrdM_AnbXT9HUssfzBbiC9on_3C4G5gZMQay3sbZ3SwEHKyTIZaer4J96DZoBZdvl_i/pub?gid=0&single=true&output=csv"
df<-read.csv(url, row.names=1, stringsAsFactor=FALSE)
```

Complete the analysis by copying the Newspaper and Radio Ads and Sales example from earlier

- Include graphics that show the scatterplots for everything you have
- Include the outputs below as one of your text cells after you run the lm the first time. Fill in the m1, m2, m3 and b (since you first have 3 x variables)
- Include the outputs below as one of your text cells after you run the lm the second time. Fill in the m1, m2, and b

Here is the structure of the data set.

```{r}
str(df)
df
```

```{r}
cor(df)
plot(df, upper.panel=NULL, pch=19)
```

```{r}
model1 <- lm(Sales ~ Floor + Dist + Age, data=df)
summary(model1)
```

Test for overall significant of linear relationship:

$$ \text{p-value} = 0.000276 $$

p-value for Floor:

$$ \text{p-value} = 0.00067 $$

p-value for Dist:

$$ \text{p-value} = 0.00661 $$

p-value for Age:

$$ \text{p-value} = 0.50218 $$

So we need to exclude Age from the model and rerun the analysis:

```{r}
model2 <- lm(Sales ~ Floor+ Dist, data=df)
summary(model2)
```

Test for overall significant of linear relationship:

$$ \text{p-value} = 0.0000384 $$

p-value for Floor:

$$ \text{p-value} = 0.00029 $$ 

p-value for Dist:

$$ \text{p-value} = 0.00330 $$ 

The regression equation would be:

$$ Sales = 41.5135(Floor) -0.3409(Dist) + 65.3239 $$   
    
The standard error is:

$$ \text{standard error} = 24.4 $$ 


