---
title: "Basics"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r, include=FALSE}
solution<-F
```

- Create a variable `x` that has value 5 
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
x <- 5 
```

- Create a variable `y` that is equal to `12*x`
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
y <- 12*x 
```

- Define a character vector `v` that has these strings on it "yes", "no", "maybe":
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
v<- c("yes", "no", "maybe")
```

- Define a vector variable `q` that has 4,-3,-2,2,3 on it. 
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
q<- c(4,-3,-2,3) 
```

Next create a dataframe for this data:

|  name  |  major | gpa |  phone    |
|:------:|:----:|:---:|:------------:|
| William |  ITM | 2.4 | 326 2375 |
| Sandy |  TDM | 3.4 | 231 3040 |
| Joan |  FBM | 3.1 | 342 3023 |

 - create a dataframe for this data
```{r, eval=FALSE, include=!solution}
name<-CODE
major<-CODE
gpa<-CODE
phone<-CODE
df <- data.frame(CODE,CODE,CODE,CODE) 
```
```{r, include=solution}
name<-c("William", "Sandy", "Joan")
major<-c("ITM", "TDM", "FBM")
gpa<-c(2.4, 3.4, 3.1) 
phone<-c("326 1375", "231 3640", "342 3023")
df <- data.frame(name,major,gpa,phone) 
```

- Print out the structure of your data frame using `str`
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
str(df)
```

- Print out just the phone column using $ sign: (Replace CODE below with the right column name for this. 
```{r, eval=FALSE, include=!solution}
df$CODE
```
```{r, include=solution}
df$phone
```

- Now print out the first few lines of the data frame using `head`
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
head(df)
```

- Use `summary(df)` to print out a summary of the data frame data:
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
summary(df)
```

- Delete the column "gpa" from the data frame:
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
df$gpa <- NULL
```

- Print out the structure of your data frame showing the column above removed: 

```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
str(df)
```

Finally add a column called "id" 
Your data frame will look like this after doing this:  

|  name  |  major | phone    | id
|:------:|:----:|:---:|:------------:|
| William |  ITM | 326 2375 | 1001 |
| Sandy |  TDM | 231 3040 | 1002 | 
| Joan |  FBM | 342 3023 | 1003 |

- add a column called "id" 
```{r, eval=FALSE, include=!solution}
df$id <- CODE 
```
```{r, include=solution}
df$id <- c(1001,1002,1003)
```

- Print out the structure of the new data frame using `str`:
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
str(df)
```

- Change Sandy's id in the dataframe to be `1004`
```{r, eval=FALSE, include=!solution}
CODE 
```
```{r, include=solution}
df[2,4] <- 1004 
```

- Print out the data frame using `head` to make sure her id is changed:
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
head(df)
```
