---
title: "Calculator"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

R can do calculations, just like a calculator:

Addition:
 
```{r}
3+4
```

Multiplication:

```{r}
3*4
```

Subtraction:
```{r}
3-4
```

Division:
```{r}
3/4
```

Exponents:
```{r}
10^2
```

Remember  $10^2=10(10)=100$

```{r}
3^4
```

This is 3 raised to the power 4. Remember $3^4=(3)(3)(3)(3)=81$ 

```{r}
3*3*3*3
```

You can call functions, like taking a square root.  

`sqrt(16)` means the same as: 
$$ \sqrt{ 16 } $$
which we know is just 4.

```{r}
sqrt(16)
```

Square root works for any non-negative number: 

```{r}
sqrt(2)
```

What happens if we try to make R take the square root of a negative number?

```{r}
sqrt(-25)
```

It gives us a warning. `NaNs produced`. NaN stands for "Not a Number", so this is telling us that R does not know how to do this. The answer is not a number. Usually this is a sign of a mistake we have made entering in what we passed to the `sqrt` function. 

You can call the round function:  
```{r}
round(6.3)
```

You can call the ceiling function, what do you think this does?  
```{r}
ceiling(6.3)
```

You can call the floor function, what does this do?  
```{r}
floor(6.8)
```

R knows about the number $\pi$ as well. It is built in:  
```{r}
pi
```

R has a remainder function. This just gives the remainder of $17/5$, which is $2$ since $17/5=3$ with remainder 2:   
```{r}
17%%5
```

This log gives us a number so that when 10 is raised to that number we get 1000. So $10^3 = 1000$, which we know is true.

Just to prove this let's raise 10 to that power:

```{r}
10^(3)
```

Order of operations 
```{r}
2+3*4
```

Just like we were taught for PEMDAS, it does the multiplication first, then the addition. This is sort of like there are parentheses around the multiplication: 
```{r}
2+(3*4)
```

If we want to make R do the addition first we can. We have to tell it to do that first using parentheses 
```{r}
(2+3)*4
```

