---
title: "Data Types"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

Variables and expressions in R have data types. The following charts shows the main data types:

|  Data Type	     |  R version     | Examples    |
|--------------------|------------------|------------|
|  decimal (number)  |   numeric      |  2.32,-0.45  | 
|  string (text)     |   character    | "hello", "k" |
|  integer             |   integer      |  12L        |
|  boolean(true/false) |   logical      |  TRUE,FALSE   |

You can find out what data type a variable holds by using the `class` function.   

`class` is a function that gives info on the data type of an object.

### Numeric 

The data type of numbers like 3.2, -2.34, 0.0 is numeric

The following variable has data type numeric:  

```{r}
x<-3.2
class(x)
```

### Character

The data type of a text or string is character.    

Examples are "Bob", "We are the champions", "Fee Fi Fo" 

```{r}
y<-"hi there"
class(y)
z<-"XXXYYYZZZ"
class(z)
```

### Logical 

The data type of something that holds 'TRUE' or 'FALSE' is 'logical'.   

This is Rs name for booleans, things that can just be TRUE or FALSE.  


```{r}
u<-TRUE
class(u)
v<-FALSE
class(v)
```

### Integer 

There is also a type for integers (..., -3,-2,-1,0,1,2,3,...), it is not used as frequently as "numeric".   

To create an integer type, you have to use an L after the integer:   

```{r}
a<-3L
class(a)
```

If you do not use an L, then R will make it a 'numeric' type:
```{r}
b<-3
class(b)
```

## Checking Types

There are functions for checking the type of a variable or expression, which are sometimes more convenient than using the `class` function. Each of these answers `TRUE` or `FALSE` depending on whether the value is that type or not:

|  Checking types    |  function     | Example    |
|--------------------|------------------|------------|
|  decimal number      |   is.numeric   |  is.numeric(2.32)  | 
|  string              |   is.character | is.character("hello")  |
|  integer             |   is.integer      |  is.integer(2L)        |
|  boolean(true/false) |   is.logical      |  is.logical(TRUE)      |


It turns out that an integer is also a numeric type
```{r}
b<-3L
is.integer(b)
is.numeric(b)
```

But 'numeric' variables are not necessarily 'integer' types. 3.4 is not an integer, and `is.integer` returns `FALSE`
```{r}
c<-3.4
is.numeric(c)
is.integer(c)
```

## Converting Types

You can change a variables type if you need to using these functions:

|  Changing types    |  function     | Example    |
|--------------------|------------------|------------|
|  decimal number      |   as.numeric   |  as.numeric(2L)  | 
|  string              |   as.character | as.character(123)  |
|  integer             |   as.integer      |  as.integer(2.0)    |
|  boolean(true/false) |   as.logical      |  as.logical(1)      |

### Character to Numeric

One use for this is to convert a string like "1.23" to a number 1.23. This happens frequently since when we read in data from files, even though the file may contain numbers, they will often be strings to begin with.

With quotes around it, a number will be seen as a string. Here is an example:

```{r}
myData<-"1.23"
is.character(myData)
is.numeric(myData)
```

So if we want to change the string "1.23" to a number, we must use `as.numeric` to convert the string to a number:

```{r}
myOtherData<-as.numeric(myData)
is.numeric(myOtherData)
myOtherData
```

### Numeric to Character

The other direction from number to a string happens sometimes as well. 

Below we create a number, then convert it to a string.

```{r}
aNumber<-4.56
aString<-as.character(aNumber)
is.character(aString)
```

## `str` function

There is another important function called `str` which gives information about the data type of something when you pass it into this function. The `str` is short for "structure".

```{r}
a<-"hi there"
str(a)
```

This code is saying that `a` is a character type and the value of it is "hi there".

```{r}
b<-5.67
str(b)
```

This code is saying that `b` is a numeric type and the value of it is 5.67.

```{r}
c<-FALSE
str(c)
```

This code is saying that `c` is a logical (boolean) type and the value of it is FALSE 
