---
title: "Data Frames"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

Data frames are the most used data structure in R. They are essentially equivalent to the rows and columns in a spreadsheet. Each row is a different record from a set of records, and each column in a different attribute or property from that set of records. 

In R the columns are vectors, and so each element in a particular column is the same data type.

Lets start with a simple example that has data describing the Day, Date and Temperature for some area:

```{r}
Day <- c("Saturday", "Sunday", "Monday", "Tuesday", "Wednesday")
Date <- c("Jul 4", "Jul 5", "Jul 6", "Jul 7", "Jul 8")
Temp <- c(75, 86, 83, 83, 87)
```

Notice how each vector has the same length. This is important when you are creating Data frames.

```{r}
length(Day)
length(Date)
length(Temp)
```

So these will be the 3 columns in this data frame. One for the day of the week, one for the date, and one for the temperature that day:

```{r}
weather <- data.frame(Day, Date, Temp)
str(weather)
```

We can see that R does not know that the factor Day should have 7 levels. That might be okay, depends on what we are doing with the data.

```{r}
weather
```

If we try to create a data frame with different length vectors, we get an error message.

Here we try it with a vector of length 5 and one of length 2.

```{r, error=TRUE}
data.frame(x = 1:5, y = 1:2) 
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}

```

```{r}
```

```{r}
```


```{r}
```

```{r}
