---
title: "Data Frames Workout"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---
```{r, include=FALSE}
blanks<-TRUE
solution<-TRUE
```

Create a dataframe for this data:

|  Name  |  GPA | Major |  phone    |
|:------:|:----:|:---:|:------------:|
| Alexa |  3.7 | FBM | 212 398 2375 |
| Tanya |  3.6 | AMC | 212 323 3040 |
| Hubert |  3.4 | FBM | 718 232 9392 |

Call the data frame `myDataFrame`:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame <- data.frame(Name=c("Robert", "Tanya", "Hubert"),
			  GPA=c(2.4, 3.2, 3.9),
			  Major=c("FBM", "AMC", "FBM"),
			  Phone=c("212 398 2375", "212 323 3040", "718 232 9392"),
			  stringsAsFactors=FALSE)
```

Print out the structure of your data frame using `str`

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
str(myDataFrame)
```

Find the dimensions of your data

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
dim(myDataFrame)
```

Now print out the first 6 lines of the data frame using `head`

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
head(myDataFrame)
```

Use a dollar sign to access and print out just the `GPA` column: 

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame$GPA
```

Use a dollar sign to access and print out just the `Phone` column: 

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame$Phone
```

Make sure that: 

1.  Major is a "factor"  
1.  Phone is "character"
1.  Name is "character"
1.  GPA is "numeric"

(Redefine some columns below if you need to using `as.character` or `as.factor`)

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame$Major <- as.factor(myDataFrame$Major)
```

Print out the (new) structure of your data frame using `str`

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
str(myDataFrame)
```
