---
title: "Data Frames"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

Data frames are the most used data structure in R. They are essentially equivalent to the rows and columns in a spreadsheet. Each row is a different record from a set of records, and each column in a different attribute or property from that set of records. 

In R the columns are vectors, and so each element in a particular column is the same data type.

Here is an example

```{r}
name <- c("James", "Sally", "Rupert", "Octavia", "Belinda") 
age <- c(23, 43, 19, 21, 33) 
isStudent <- c(TRUE, FALSE, TRUE, TRUE, FALSE)
favColor <- c("red", "green", "blue", "yellow", "orange")

customers <- data.frame(name, age, isStudent, favColor)
```

Notice how each vector has the same length. This is important when you are creating Data frames.

```{r}
length(name)
length(age)
length(isStudent)
length(favColor)
```

If we try to create a data frame with different length vectors, we get an error message.

Here we try it with a vector of length 5 and one of length 2.

```{r, error=TRUE}
data.frame(x = 1:5, y = 1:2) 
```

Lets look at the first few items in the data frame

```{r}
head(customers)
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```


```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}

```

```{r}
```

```{r}
```


```{r}
```

```{r}
