---
title: "Data Frames"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

Data frames are the most used data structure in R. They are essentially equivalent to the rows and columns in a spreadsheet. Each row is a different record from a set of records, and each column is a different attribute or property from that set of records. 

| name    | age | isStudent | favColor |
|---------|-----|-----------|----------|
| James   | 23  | TRUE      | red      |
| Sally   | 43  | FALSE     | green    |
| Rupert  | 19  | TRUE      | blue     |
| Octavia | 21  | TRUE      | yellow   |
| Belinda | 33  | FALSE     | orange   |

In R the columns are vectors, and so each element in a particular column is the same data type.

Here is an example where the different columns are given by 4 vectors:

```{r}
name <- c("James", "Sally", "Rupert", "Octavia", "Belinda") 
age <- c(23, 43, 19, 21, 33) 
isStudent <- c(TRUE, FALSE, TRUE, TRUE, FALSE)
favColor <- c("red", "green", "blue", "yellow", "orange")

customers <- data.frame(name, 
                        age, 
                        isStudent, 
                        favColor, 
                        stringsAsFactors=FALSE)
```

Notice how each vector has the same length. This is important when you are creating Data frames.

```{r}
length(name)
length(age)
length(isStudent)
length(favColor)
```

What does the structure of the data frame look like:

```{r}
str(customers)
```

Lets look at the first few items in the data frame

```{r}
head(customers)
```

If we try to create a data frame with different length vectors, we get an error message.

Here we try it with a vector of length 5 and one of length 2.

```{r, error=TRUE}
data.frame(x = c(1,2,3,4,5), y = c(1,2)) 
```

Now there are various ways to refer to the rows and the columns in a data frame. Each of the columns we can refer to by using a dollar sign. Here is the name column:

```{r}
customers$name
```

And the ages column:

```{r}
customers$age
```

You can remove a column of data by just setting it to NULL:

```{r}
customers$favColor <- NULL
str(customers)
```

You can add a column of data by just setting it as one of the fields of the data frame:

```{r}
favMusic <- c("jazz", "classical", "electronic", "country", "electronic")
customers$favMusic <- favMusic 
str(customers)
```

Finally you can get some info on the data in a data frame:

```{r}
summary(customers)
```

You can see here that is shows the mean age is 27.8 and the min and the max of the ages are 19 and 43. There are 3 who are students and 2 who are not. For name and favMusic there is not much it can tell us. It says those are "character" types and there are 5 of them. 


We can also refer to one particular entry in the data frame by using indices. The first index is for the row and the second index is for the column.

For example this is the entry in the 2nd row and the 3rd column:

```{r}
customers[2,3]
```

Here is the entry for the 4th row and the 1st column:

```{r}
customers[4,1]
```

This is the 2nd row in its entirety:

```{r}
customers[2,]
```
