---
title: "Data Types In Class"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r include=F}
ex<-T
```
- Assign a variable using `myNumeric<-1.2`
- Print out info on `myNumeric` using the `str` function

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
myNumeric<-1.2
str(myNumeric)
```

This should output the shorthand `num` which means `numeric`

- Use the `is.numeric` function to check if `myNumeric` is a numeric data type.

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
is.numeric(myNumeric)
```

The output should be `TRUE` since `myNumeric` is a numeric data type.

Lets look at string types

- Assign a variable using `myString<-"hello"`
- Print out info on `myString` using the `str` function

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
myString<-"hello"
str(myString)
```
This should output the shorthand `chr` which means `character`

- Use the `is.character` function to check if `myString` is a character data type 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
is.character(myString)
```
The output should be `TRUE` since `myString` is a character data type.

```{r}
```
Lets look at boolean type:

- Assign a variable using `myBoolean<-TRUE`
- Print out info on `myBoolean` using the `str` function

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
myBoolean<-TRUE
str(myBoolean)
```

This should output the shorthand `logi` which means `logical`, which is the boolean type for R.

- Use the `is.logical` function to check the data type of `myBoolean` from above 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
is.logical(myBoolean)
```
The output should be `TRUE` since `myBoolean` is a boolean data type.

One conversion that is freqently used is from at string like "1.23" to a number 1.23.

With quotes around it, a number will be seen as a string:


- Define a variable `aString<-"1.23"`
- print out whether it is a string using `is.character` 
- print out whether it is a numeric using `is.numeric` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
aString<-"1.23"
is.character(aString)
is.numeric(aString)
```

The output of `is.character(aString)` should be `TRUE` since `aString` was a string.

The output of `is.numeric(aString)` should be `FALSE` since `aString` was not a numeric.

So if we want to change the string "1.23" to a number, we must use `as.numeric` to convert the string to a number:

- Define a variable `aNumber` by using the function `as.numeric` on `aString`
- print out whether `aNumber` is a numeric using `is.numeric` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
aNumber<-as.numeric(aString)
is.numeric(aNumber)
```

The output of `is.numeric(aNumber)` should be `TRUE` since `aNumber` was a numeric.

Finally for the code below add a couple of `str` functions to display information about the variables. 

- Print out info on `x` using the `str` function
- Print out info on `y` using the `str` function

```{r include=ex, eval=F}
x<-"1.23"
y<-as.numeric("1.23")
CODE
```
```{r include=!ex}
x<-"1.23"
y<-as.numeric("1.23")
str(x)
str(y)
```

`x` is a character since there are quotations marks so that makes it a string.

`y` is numeric since it was converted to a numeric with `as.numeric`.

Once again, for the code below add a couple of `str` functions to display information about the variables. 

- Print out info on `z` using the `str` function
- Print out info on `w` using the `str` function

```{r include=ex, eval=F}
z<-"TRUE"
w<-as.logical("TRUE")
CODE
```
```{r include=!ex}
z<-"TRUE"
w<-as.logical("TRUE")
str(z)
str(w)
```

`z` is a character since there are quotations marks so that makes it a string.

`w` is numeric since there are quotations marks so that makes it a string.
