---
title: "Data Frames Workout"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---
```{r, include=FALSE}
blanks<-FALSE
solution<-TRUE
```

Create a dataframe for this data:

|  Name  |  GPA | Major |  Phone    |
|:------:|:----:|:---:|:------------:|
| Alexa |  3.7 | FBM | 212 398 2375 |
| Tanya |  3.6 | AMC | 212 323 3040 |
| Hubert |  3.4 | FBM | 718 232 9392 |

Call the data frame `myDataFrame`:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame <- data.frame(Name=c("Alexa", "Tanya", "Hubert"),
			  GPA=c(3.7, 3.6, 3.4),
			  Major=c("FBM", "AMC", "FBM"),
			  Phone=c("212 398 2375", "212 323 3040", "718 232 9392"),
			  stringsAsFactors=FALSE)
```

Print out the structure of your data frame using `str`

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
str(myDataFrame)
```

Print the number of rows with the `nrow` function

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
nrow(myDataFrame)
```

Print the number of columns with the `ncol` function

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
ncol(myDataFrame)
```

Now print out the first few lines of the data frame using `head`. In this case it will be all the data, since `head` prints the first 6 lines, and this data has less than 6 lines.

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
head(myDataFrame)
```

Use a dollar sign to access and print out just the `GPA` column: 

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame$GPA
```

Use a dollar sign to access and print out just the `Phone` column: 

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame$Phone
```

Make sure that: 

1.  Name is "character"
1.  GPA is "numeric"
1.  Major is a "factor"  
1.  Phone is "character"

(Redefine some columns below if you need to using `as.character` or `as.factor`)

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame$Major <- as.factor(myDataFrame$Major)
```

Print out the (new) structure of your data frame using `str`

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
str(myDataFrame)
```

Use the `summary` function to print out a summary of the data frame data:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
summary(myDataFrame)
```

Extract the element in the 2nd row and 3rd column by using `dataFrame[,]`, and using the right index or indices inside the square brackets: 

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame[2,3]
```

Extract the entire second row of data by using `myDataFrame[,]`, and again using the right index or indices inside the square brackets: 

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame[2,]
```

Extract the entire second column of data by using `myDataFrame[,]`, and again using the right index or indices inside the square brackets: 

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame[,2]
```

Delete the column "Major" from the data frame:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame$Major <- NULL
```

Print out the structure of your data frame showing the column above removed: 

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
str(myDataFrame)
```

Finally add a column (with data type "factor") called "ID" 
Your data frame should now look like this:  

|  Name  |  GPA |  Phone       | ID  |
|:------:|:----:|:------------:|:---:|
| Alexa |  3.7 | 212 398 2375 | 1001 |
| Tanya |  3.6 | 212 323 3040 | 1002 |
| Hubert |  3.4 | 718 232 9392 | 1003 |


```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame$ID = factor(c(1001,1002,1003))
```

Print out the structure of the new data frame using `str`:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
str(myDataFrame)
```

Print out the dataframe using `head` now:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
head(myDataFrame)
```

Use subsetting to select only those rows with `GPA > 3.5`

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame[myDataFrame$GPA  > 3.5,]
```

Try to move the last column so that it is the first column

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame <- myDataFrame[c("ID", "Name", "Phone", "GPA")]
```

Print out the data frame using `head` to make sure ID is first:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
head(myDataFrame)
```

Change Tanyas GPA in the dataframe to be `3.98`

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
myDataFrame[2,4] <- 3.98
```

Print out the data frame using `head` to make sure her GPA is changed:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
head(myDataFrame)
```
