---
title: "Data Frames Manipulations"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r include=F}
ex<-T
```

Lets look at a simple example that has data from the Poshmark website. We scraped the names of some items, the original retail, and their current offering prices for some items being offered:

Lets make the data into some vectors:

```{r}
name <- c("Jcrew blazer",           
	  "Forever 21 lace zip up blazer",                     
	  "Banana Republic Navy  Blazer",                     
	  "Julian Taylor Pant And Blazer Size 12",             
	  "Bernard Zins Paris Multi Colored Jacket",
      "Evan Picone Suit Blazer - 6",
      "Black blazer",
      "Jones Studio Blazer")  
original <- c(198,49,129,999,129,74,80,59)
offered<- c(60,29,45,30,22,13,15,25)
```

Next we will create a dataframe with the items above in it.

- create a data frame called `items` using the 3 vectors above. Replace CODE with the 3 vectors names, and use commas between them
```{r include=ex, eval=F}
items <- data.frame(CODE)
```
```{r include=!ex}
# Original:
# items <- data.frame(CODE)

# Solution:
items <- data.frame(name, original, offered)
```

- print out info on the  `items` using `str`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Original:
# CODE

# Solution:
str(items)
```

- print out all the records on `items` using `print(items)`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Original:
# CODE

# Solution:
print(items)
```

Looks like one of the values is wrong or made up: 999 is just wrong. Lets fix that to be \$54.

- change "Julian Taylor" item's price to be 54 (replace CODE with correct value)
```{r include=ex, eval=F}
items[4,2]<-CODE
```
```{r include=!ex}
# Original:
# items[4,2]<-CODE

# Solution:
items[4,2]<-54
```

Lets check to make sure this looks okay.

- print out all the records again  using `print(items)`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Original:
# CODE

# Solution:
print(items)
```

Let's calculate markdown percents. We will just calculate the `original - offered` and divide by `original`.

- assign `markdown <- (items$original-items$offered)/items$original`
- print out `markdown`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Original:
# CODE

# Solution:
markdown <- (items$original-items$offered)/items$original
markdown
```

Almost, lets round it to the nearest percent instead

- assign `markdown <- 100*round(markdown,2)`
- print out `markdown`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Original:
# CODE

# Solution:
markdown <- 100*round(markdown,2)
markdown
```

Finally lets add it as a new column to the original data frame:

- add the column to the data frame with `items$markdown<-markdown`
- print out info on the new dataframe with `str`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Original:
# CODE

# Solution:
items$markdown<-markdown 
str(items)
```

Now lets print it out:

- print out the first few records of `items` using `head`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Original:
# CODE

# Solution:
head(items)
```

We dont have that much data but you could find the average markdown:

- use `mean` to find the average, pass it `items$markdown` as argument(change CODE below)
```{r include=ex, eval=F}
mean(CODE)
```
```{r include=!ex}
# Original:
# mean(CODE)

# Solution:
mean(items$markdown)
```

For this set of data the average offered price was 66% off the original. Lets see the range of markdowns: 

- use `range` to find the range, pass it `items$markdown` as argument (change CODE below)
```{r include=ex, eval=F}
range(CODE)
```
```{r include=!ex}
# Original:
# range(CODE)

# Solution:
range(items$markdown)
```

This gives the ranges of the markdowns from this set of data 
from `r range(items$markdown)[1]`% to `r range(items$markdown)[2]`%


Lets create a model that predicts the offered price from the original:

- create a model using `lm` that predicts `offered` from the `original` (fill in CODE with the appropriate thing below)
```{r include=ex, eval=F}
model<-lm(CODE, data=items)
summary(model)
```
```{r include=!ex}
# Original:
# model<-lm(CODE, data=items)
# summary(model)

# Solution:
model<-lm(offered~original, data=items)
summary(model)
```

Find the correlation between **offered** and **original**

- find the correlation between `items$offered` and `items$original` using the function `cor` (pass `items$original` as first argument and `items$offered` as the second argument)
```{r include=ex, eval=F}
cor(CODE)
```
```{r include=!ex}
# Original:
# cor(CODE)

# Solution:
cor(items$original, items$offered)
```

Now find the scatterplot of **offered** and **original** 

- plot the scatterplot of `offered` vs `original` using `plot`. Pass `items$original` and `items$offered` as the first and second argument to `plot` 
- add the regression line using `abline`. Pass the `model` to that function.
```{r include=ex, eval=F}
plot(CODE)
abline(CODE)
```
```{r include=!ex}
# Original:
# plot(CODE)
# abline(CODE)

# Solution:
plot(items$original, items$offered)
abline(model)
```
