---
title: "Data Types In Class"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

```{r include=F}
ex<-F
```
- Assign a variable using `myNumeric<-1.2`
- Print out the data type of `myNumeric` using the `class` function

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
myNumeric<-1.2
class(myNumeric)
```

This should output the class `numeric`

- Use the `is.numeric` function to check if `myNumeric` is a numeric data type.

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
is.numeric(myNumeric)
```

The output should be `TRUE` since `myNumeric` is a numeric data type.

Lets look at string types

- Assign a variable using `myString<-"hello"`
- Print out the data type of `myString` using the `class` function

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
myString<-"hello"
class(myString)
```
The output of this should be `character`

- Use the `is.character` function to check if `myString` is a character data type 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
is.character(myString)
```
The output should be `TRUE` since `myString` is a character data type.

```{r}
```
Lets look at boolean type
- Assign a variable using `myBoolean<-TRUE`
- Print out the data type of `myBoolean` using the `class` function

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
myBoolean<-TRUE
class(myBoolean)
```

- Use the `is.logical` function to check the data type of `myBoolean` from above 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
is.logical(myBoolean)
```
The output should be `TRUE` since `myBoolean` is a boolean data type.

One conversion that is freqently used is from at string like "1.23" to a number 1.23.

With quotes around it, a number will be seen as a string:

```{r}
aString<-"1.23"
is.character(aString)
```

So if we want to change the string "1.23" to a number, we must use `as.numeric` to convert the string to a number:

```{r}
aNumber<-as.numeric(aString)
is.numeric(aNumber)
```

Finally guess the data types that will be displayed below by the 4 `class` functions:

The first one will be:
The second one will be:
The third one will be:
The fourth one will be:

```{r}
class("1.23")
class("TRUE")
x<-as.numeric("1.23")
y<-as.logical("TRUE")
class(x)
class(y)
```
