---
title: "Data Types"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

You can find out what data type a variable holds by using the `class` function. 

For the following the data type is 'numeric'. Examples are 3.2, -2.34, 0.0
 
```{r}
x<-3.2
class(x)
```

`class` is one function that gives info on the data type of an object. Another interesting function is called `str`.  

This function is called the "structure" function and and also gives information about the object you pass to it.   
Lets see what it gives here: 

```{r}
str(x)
```

This says that  `x` is a numeric type and has value 3.2.

The data type of a text or string is 'character'.    

Examples are "Bob", "We are the champions", "Fee Fi Fo" 

```{r}
y<-"hello there"
class(y)
z<-"XXXYYYZZZ"
class(z)
```

```{r include=FALSE, eval=FALSE}
knitr::knit_exit()
```

The data type of something that holds 'TRUE' or 'FALSE' is 'logical'.   
This is Rs name for Booleans, things that can just be TRUE or FALSE.  


```{r}
z<-TRUE
r<-FALSE
class(z)
class(r)
```

There is also a type for integers (..., -3,-2,-1,0,1,2,3,...), it is not used as frequently as "numeric".   

To create a integer type, you have to use an L after the integer:   

```{r}
a<-3L
class(a)
```

If you do not use an L, then R will make it a 'numeric' type:
```{r}
b<-3
class(3)
```

It turns out that an integer is also a numeric type
```{r}
b<-3L
is.integer(b)
is.numeric(b)
```

But not 'numeric' variables are not necessarily 'integer' types. 3.4 is not an integer, is `is.integer` returns `FALSE`
```{r}
c<-3.4
is.numeric(c)
is.integer(c)
```

You can change a variables type if you need to using these functions:

1.  `as.numeric` to make it a numeric
1.  `as.integer` to make it an integer
1.  `as.character` to make it a string 
1.  `as.logical` to make it a boolean

Below we make the variable `a`, which starts as an 'integer' into a 'numeric'. We just re-assign it to do so.
```{r}
a<-3L
is.integer(a)
a<-as.numeric(a)
is.numeric(a)
is.integer(a)
```

One reason for having types is so that R can check if you are doing things that make sense.  
For example adding two numeric types makes sense
```{r}
d<-3.4
e<-4.23
d+e
```

But adding two strings (with type 'character') does not:
```{r,error=TRUE}
f<-"Goodbye"
g<-"Cruel World"
f+g
```

The error is telling us we cannot use `+` on two strings

Lets try adding an 'integer' and a 'numeric'

```{r}
h<-3L
i<-2.3
h+i
```

That seems to work fine.

Finally what happens if we add a 'numeric' and a 'character' type: 

```{r, error=TRUE}
k<-3.2
l<-"hello"
k+l
```

