---
title: "Data Frames InClass"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---
```{r, include=FALSE}
ex<-T
```

Create a dataframe for this data:

|  Name  |  GPA | Major |  Phone    |
|:------:|:----:|:---:|:------------:|
| Alexa |  3.7 | FBM | 212 398 2375 |
| Tanya |  3.6 | AMC | 212 323 3040 |
| Hubert |  3.4 | FBM | 718 232 9392 |

- Create a data frame `df` by using the `data.frame` function. 
- You will need to make some appropriate vectors to be the columns of your dataframe. Replace the word `CODE` below with the appropriate vector using the function `c` 
- Use the argument `stringsAsFactors=FALSE` in your data.frame function:

```{r, eval=FALSE, include=ex}
df <- data.frame(Name = CODE,
			  GPA = CODE,
			  Major = CODE,
			  Phone = CODE,
			  stringsAsFactors=FALSE)
```
```{r, include=!ex}
# Original
# df <- data.frame(Name = CODE,
# 			  GPA = CODE,
# 			  Major = CODE,
# 			  Phone = CODE,
# 			  stringsAsFactors=FALSE)
df <- data.frame(Name=c("Alexa", "Tanya", "Hubert"),
			  GPA=c(3.7, 3.6, 3.4),
			  Major=c("FBM", "AMC", "FBM"),
			  Phone=c("212 398 2375", "212 323 3040", "718 232 9392"),
			  stringsAsFactors=FALSE)
```

- Print out the structure of your data frame using `str`

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
str(df)
```

- Print out just the GPA column using $ sign `df$GPA`  

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
df$GPA
```


- Print out just the Phone column using $ sign `df$Phone`:  

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
df$Phone
```
Now print out the first few lines of the data frame using `head(df)`. In this case it will be all the data, since `head` prints the first 6 lines, and this data has less than 6 lines.

- Print out your dataframe using `head(df)`

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
head(df)
```

- Use `summary(df)` to print out a summary of the data frame data:

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
summary(df)
```

- Delete the column "Major" from the data frame (use `df$Major<-NULL`)

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
df$Major <- NULL
```

- Print out the structure of your data frame showing the column above removed: 

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
str(df)
```

Finally add a column called "ID" 
Your data frame should now look like this:  

|  Name  |  GPA |  Phone       | ID  |
|:------:|:----:|:------------:|:---:|
| Alexa |  3.7 | 212 398 2375 | 1001 |
| Tanya |  3.6 | 212 323 3040 | 1002 |
| Hubert |  3.4 | 718 232 9392 | 1003 |


- Add a column using `df$ID<-c(1001,1002,1003)`

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
df$ID <- c(1001,1002,1003)
```

- Print out the structure of the new data frame using `str`:

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
str(df)
```

- Change Tanyas GPA in the dataframe to be `3.98`

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
df[2,4] <- 3.98
```

- Print out the data frame using `head` to make sure her GPA is changed:

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
head(df)
```

- Extract (print out) the element in the 2nd row and 3rd column by using `df[,]`, and using the right index or indices inside the square brackets: 

```{r, eval=FALSE, include=ex}
PUT CODE HERE
```
```{r, include=!ex}
df[2,3]
```
