---
title: "Diamonds Carat Clarity"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

Here is some data for Diamonds

```{r include=F}
ex<-T
```

- Run this first to set nice print outs
```{r}
options("scipen"=100, "digits"=4)
```

| carat | clarity | price |
|-|-|-|
| 0.71 | 3 | 2554 |
| 0.72 | 5 | 2691 |
| 0.33 | 4 | 854 |
| 1.52 | 4 | 9576 |
| 1.23 | 4 | 9116 |
| 0.54 | 6 | 1829 |
| 0.32 | 5 | 828 |
| 1.31 | 3 | 8767 |
| 1.11 | 2 | 5648 |
| 1.03 | 2 | 4283 |
| 0.56 | 5 | 1131 |
| 1.29 | 2 | 5601 |
| 0.53 | 5 | 1577 |
| 1.7 | 5 | 11257 |
| 0.3 | 4 | 615 |

- create a data `df` using the vectors
```{r include=ex, eval=F}
carat<-c(0.71,0.72,0.33,1.52,1.23,0.54,0.32,1.31,1.11,1.03,0.56,1.29,0.53,1.7, 0.3) 
clarity<-c(3,5,4,4,4,6,5,3,2,2,5,2,5,5,4)
price<-c(2554,2691,854,9576,9116,1829,828,8767,5648,4283,1131,5601,1577,11257,615)
df<-data.frame(CODE)
```
```{r include=!ex}
carat<-c(0.71,0.72,0.33,1.52,1.23,0.54,0.32,1.31,1.11,1.03,0.56,1.29,0.53,1.7, 0.3) 
clarity<-c(3,5,4,4,4,6,5,3,2,2,5,2,5,5,4)
price<-c(2554,2691,854,9576,9116,1829,828,8767,5648,4283,1131,5601,1577,11257,615)
df<-data.frame(carat,clarity, price)
```

- print out info for the dataframe using `str` 
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
str(df)
```

- print out the first few rows in the dataframe use `head` 
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
head(df)
```

- create scatterplots of the columns  `plot(df, upper.panel=NULL, pch=19)` 
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
plot(df, upper.panel=NULL, pch=19)
```

- create correlation matrix for `df` using the code `cor(df)` 
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
cor(df)
```

- run a linear regression model using `carat` and `clarity` to predict `price` 
```{r include=ex, eval=F}
model1<-lm(CODE,data=df)
summary(model1)
```
```{r include=!ex}
model1<-lm(price~carat+clarity,,data=df)
summary(model1)
```

**Test for overall significant of linear relationship:**

overall p-value = ????

**Clarity:**

p-value for clarity = ???

**Carat:**

p-value for carat = ???

Eliminate Clarity from the model:

- run a new linear regression model using `carat` to predict `price` 

```{r include=ex, eval=F}
model2<-lm(CODE,data=df)
summary(model2)
```
```{r include=!ex}
model2<-lm(price~carat,,data=df)
summary(model2)
```

Fill in the ??? below with the right value:

**Test for overall significant:**

overall p = ??? 

**The regression equation is this:**

price =???(carat) + ???   

**The standard error is:**

std error = ???

Make predictions when: 

- carat is 1.3
- carat is 0.6 
- carat is 1.8 
    
To do this:

- assign a vector `carat` to hold the predictors above (replace CODE below)
- create a dataframe called `predictors` using the `carat` vector  
- print out the `predictors` dataframe  
```{r include=ex, eval=F}
carat<-CODE
predictors <- data.frame(carat)
predictors
```
```{r include=!ex}
carat<-c(1.3,0.6,1.8)
predictors <- data.frame(carat)
predictors
```

Now lets do the predictions:

- make predictions using the `predict` function passing in the `model2` and the `predictors` dataframe you just made (pass 2 arguments where you see CODE)
- print out the `predictions`
```{r include=ex, eval=F}
predictions<-predict(CODE)
predictions
```
```{r include=!ex}
predictions<-predict(model2, predictors)
predictions
```

Fill in the correct answers below:

- Prediction when `carat` is 1.3: ???
- Prediction when `carat` is 0.6: ???
- Prediction when `carat` is 1.8: ???

