---
title: "Elasticity and Maximizing Profits"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---
This notebook is an expanded version of the analysis done here: 
[Price Elasticity with R](http://www.salemmarafi.com/code/price-elasticity-with-r)   

Also you can see this page as well for a similar version:
[Pricing Analysis Example](https://rstudio-pubs-static.s3.amazonaws.com/185880_f9e3e3ee84314609b531524dfa3f4f1b.html) 

First make sure RCurl is installed.

```{r eval=FALSE}
install.packages("RCurl")
```

Then make sure it is loaded:

```{r}
library("RCurl")
```

We use the getURL function from the RCurl package to load the data from the website. It is returned to us as a text string. 

```{r}
url<- "http://www.salemmarafi.com/wp-content/uploads/2014/06/supermarket.csv"
textString<-getURL(url)
df<-read.csv(text=textString)
```

Here is the structure of the data set.

```{r}
str(df)
```

First we have 30 observations for demand and price for eggs. Then we have 30 observations of the ad type that was run, where 0 means featured the cookies poster and 1 means featured the eggs poster. Finally we have data on the price of cookies.  

Here is the data: 

```{r}
df
```

Let's start with a summary of the data:  

```{r}
summary(df)
```

The mean demand is `r mean(df$Sales)` and the mean price is about \$`r mean(df$Price.Eggs)`   

Lets look at the distribution of demand. 

```{r}
par(mfrow=c(1,2))
boxplot(df$Sales,main="Boxplot for Egg Sales", xlab="Egg Sales")
hist(df$Sales,main='Histogram for Egg Sales',xlab='Egg Sales',prob=T)
```

There are no outliers or other unusual data to speak of here. 

Lets look at the correlations between the variables.

```{r}
cor(df)
pairs(df, pch=20)
```

It looks like there is a strong correlation between sales and own price. We expected that of course.

There is a weaker correlation between egg sales and price of cookies. 

Let's model using all the predictors:
 
```{r}
model <- lm(Sales~Price.Eggs+Ad.Type+Price.Cookies, df)
summary(model)
b<-round(unname(coefficients(model)),2)
b
```

This shows the coefficients for the various predictors. 

Price of eggs, the ad type and price of cookies are all significant with p-value less than .05.    

The multiple regression equation is:    

```{r echo=FALSE}
    B<-round(b,2);
    op2 <- ifelse(B[2]<0,"","+");
    op3 <- ifelse(B[3]<0,"","+");
    op4 <- ifelse(B[4]<0,"","+");
```
$$
    Q = `r B[1]` `r op2` 
        `r B[2]`(P_{eggs}) `r op3` 
	`r B[3]`(AdType) `r op4` 
	`r B[4]`(P_{cookies}) 
$$

Next we show the calculation of the price elasticity: For price elasticity we compute the percent change in quantity divided by the percent change in price. 

$$
\text{Price Elasticity} = \frac{\frac{\Delta Q}{Q}}{\frac{\Delta P_{eggs}}{P_{eggs}}}
			=(\frac{\Delta Q}{\Delta P_{eggs}})(\frac{P_{eggs}}{Q})
$$

For the first part $\frac{\Delta Q}{\Delta P_{eggs}}$, this is just the multiple regression coefficient describing the rate of change of $Q$ as $P_{eggs}$ changes. That is actually just the coefficient from the multiple regression equation! So that is just $b[2] = `r b[2]`$. For $\frac{P_{eggs}}{Q}$, we will use the mean of the price of eggs and the mean of sales which we saw in the summary of the data above for that. 

Let's compute the values:

```{r}
priceEggs <- mean(df$Price.Eggs)
priceEggs
quantity <- mean(df$Sales)
quantity
priceElasticity <- b[2]* (priceEggs/quantity)
priceElasticity
```

The equation looks like this: 

```{r echo=FALSE}
    B<-round(b,2);
    P<- round(priceEggs,2);
    Q <- round(quantity,2);
    PE <- round(priceElasticity, 2);
```
$$
\text{PriceElasticity} =
    \frac{ \frac{\Delta Q}{Q} }{ \frac{\Delta P_{eggs}}{P_{eggs}} } =
    \frac{\Delta Q}{\Delta P_{eggs}} \frac{P_{eggs}}{Q} =
    (`r B[2]`)(\frac{`r P`}{`r Q`}) =
    `r PE`
$$

This suggests that a 1% decrease in price of eggs will increase egg sales by 2.4%.

Next is the calculation of the Cross Price Elasticity: For cross-price elasticity of eggs with cookies we compute the percent change in quantity of eggs divided by the percent change in the price of cookies: 

```{r}
PriceCookies <- mean(df$Price.Cookies)
Quantity <- mean(df$Sales)
CrossPriceElasticity <- b[4]*PriceCookies/Quantity
CrossPriceElasticity
```

The equation looks like this: 

```{r echo=FALSE}
    B<-round(b,2);
    P <- round(PriceCookies,2);
    Q <- round(Quantity,2);
    CPE <- round(CrossPriceElasticity, 2);
```
$$
\text{CrossPriceElasticity} =
    \frac{ \frac{\Delta Q}{Q} }{ \frac{\Delta P_{cookies}}{P_{cookies}} } =
    \frac{\Delta Q}{\Delta P_{cookies}} \frac{P_{cookies}}{Q} =
    (`r B[4]`)(\frac{`r P`}{`r Q`}) =
    `r CPE`
$$

This suggests that 1% decrease in cookies price will increase the egg sales by 1.3%, and that cookies and eggs are compliments.

```{r echo=FALSE}
meanCookies <- round(mean(df$Price.Cookies),2)
```
For setting the optimal price we need some values for $P_{cookies}$ and $AdType$. Suppose the current cookies price is $P_{cookies}=`r meanCookies`$ and the $AdType = 0$ for featuring the cookies. We plug these into the multiple regression equation:

```{r echo=FALSE}
    B<-round(b,2);
    op2 <- ifelse(B[2]<0,"","+");
    op3 <- ifelse(B[3]<0,"","+");
    op4 <- ifelse(B[4]<0,"","+");
```
$$
    Q = `r B[1]` `r op2` 
        `r B[2]`(P_{eggs}) `r op3` 
	`r B[3]`(0) `r op4` 
	`r B[4]`(`r meanCookies`) 
$$

So the slope and intercept for the simplified demand equation we will use is this:

```{r}
slope<- b[2]
slope
intercept <- b[1] + b[4]*PriceCookies
intercept
```

So our new equation is just this:

```{r echo=FALSE}
eqnIntercept <- round(intercept,2)
eqnSlope<-round(slope,2)
```
$$   
Q  = `r eqnIntercept` `r op2` `r eqnSlope`(P_{eggs})
$$

Suppose the unit cost of eggs is $1.50. Then here is the profit function:

```{r}
profit <- function(p) {
    (p-1.50)*(intercept+slope*p)
}
curve(profit, from=0, to =8, main="Profit Function", xlab="Price", ylab="Profit")
```

Finally we optimize the profit function:

```{r}
optimize(profit, lower=0, upper=8, maximum=TRUE)
```

The maximum profit occurs when the price is \$3.83 and the Profit is \$87.53.

So we would advise to set the price of eggs to \$3.83
