---
title: "KMeans"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r echo=T, results='hide', message=F, warning=F}
options("scipen"=100, "digits"=4)
if(!require("readr")) install.packages("readr")
if(!require("Metrics")) install.packages("Metrics")
library("Metrics")
library("readr")
```

This simple example is taken from [KMeans Clustering](https://www.guru99.com/r-k-means-clustering.html)

Suppose we have the age of some customers and the amount they spent on an online retail website for a month. Can we get an idea of what kinds of groups we have here? We would like to cluster the data in some way.

```{r}
age = c(18, 21, 22, 24, 26, 26, 27, 30, 31, 35, 39, 40, 41, 42, 44, 46, 47, 48, 49, 54)
spent= c(10, 11, 22, 15, 12, 13, 14, 33, 39, 37, 44, 27, 29, 20, 28, 21, 30, 31, 23, 24)
plot(age, spent, pch=19)
```

It looks like maybe there are 2 or 3 clusters.  

Lets create a dataframe with this data:

```{r}
df <- data.frame(age = age, spent=spent)
str(df)
```

Lets print out a little of the dataframe:

```{r}
head(df)
```

Now lets go ahead and use `kmeans` with K=2 and see what it finds.

```{r}
set.seed(2)
model<-kmeans(df,2, nstart=20)
```

Lets show each point according to the cluster it has been added to and also add the centers in blue.

```{r}
plot(age, spent, col=model$cluster, pch=19)
points(model$centers, pch=19, col="blue")
```

Now we add a column to the dataframe `df` to show which cluster each of the points in the data set belong to: 

```{r}
df$cluster <- model$cluster
print(df)
```

The cluster column is either 1 or 2 depending on which cluster the algorithm assigned the data point.


What about if we wanted to try 3 clusters. Lets run `kmeans` again with K=3:

```{r}
set.seed(3)
model<-kmeans(df,3, nstart=20)
```

Lets show each point according to the cluster it has been added to and also add the centers in blue.

```{r}
plot(age, spent, col=model$cluster, pch=19)
points(model$centers, pch=19, col="blue")
```

Now we set the column `cluster` to show the current cluster: 

```{r}
df$cluster <- model$cluster
print(df)
```

With 3 groups of customers we found these three groups:

1. Those that are younger and spend less
1. Those that are middle age and spend more 
1. Those that are older age and spend midrange between more and less 

