---
title: "Magic Fizz"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

Run this code block to set things up:

```{r}
url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQhffJe1DftYdhSqfznMvmO5l_0S9z0sf_PN8NAn1XExaLjlIc-HQcYgry10iphx9egxGtjBqOCcEEB/pub?gid=897298122&single=true&output=csv"
df<-read.csv(url)
```

```{r include=F}
ex<-T
```

The above loads in some data collected from 20 respondents to a survey about a new soft drink called **MagicFizz**. Each of the respondents rated the drink for each of the categories `Flavor` ,`Texture` `FizzSensation` and `PackageDesign` and also for `OverallSatisfaction`.

The data frame `df` is loaded with all the responses. 

The goal here is to try to predict `OverallSatisfaction` from the rest of the variables.

- print out some info on `df` using `str(df)`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Orig:
# CODE

# Solution:
str(df)
```

- print out `df` using `print(df)`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Orig:
# CODE

# Solution:
print(df)
```

- print out the correlation matrix for df using `cor(df)` 
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Orig:
# CODE

# Solution:
cor(df)
```

FILL IN THE ???? below with the right values from above:

Correlation:    

- between `Flavor` and `Texture` ??? 
- between `Flavor` and `OverallSatisfaction` ??? 
- between `Texture` and `OverallSatisfaction` ??? 
- between `FizzSensation` and `OverallSatisfaction` ??? 
- between `PackageDesign` and `OveralllSatisfaction` ??? 

Let's run our regression model using all the variables:

- assign `model1` the result of `lm`, using `OverallSatisfaction ~ Flavor + Texture + FizzSensation + PackageDesign` as the first argument to `lm` and then `data=df` as the second argument
- call `summary(model1)` to print out the regression model info after creating the model
```{r include=ex, eval=F}
model1 <- lm(CODE, data=df)
summary(model1)
```
```{r include=!ex}
# Orig:
# model1 <- lm(CODE, data=df)
# summary(model1)

# Solution:
model1 <- lm(OverallSatisfaction ~ Flavor+Texture+FizzSensation+PackageDesign, data=df)
summary(model1)
```

FILL IN THE ???? below with the right values from above:

**Test for overall significant of linear relationship:**

overall p-value = ????

**Texture:**

p-value for Texture = ???

**Flavor:**

p-value for Flavor= ???

**FizzSensation:**

p-value for FizzSensation= ???

**PackageDesign:**

p-value for PackageDesign= ???

Eliminate the `Texture` variable, since it has the highest p-value.

Then run the regression again:

- assign `model2` the result of `lm`, using `OverallSatisfaction ~ Flavor + FizzSensation + PackageDesign` as the first argument to `lm` and then `data=df` as the second argument
- call `summary(model2)` to print out the regression model info after creating the model
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Orig:
# CODE 

# Solution:
model2 <- lm(OverallSatisfaction ~ Flavor+FizzSensation+PackageDesign, data=df)
summary(model2)
```

FILL IN THE ???? below with the right values from above:

**Test for overall significant of linear relationship:**

overall p-value = ????

**Flavor:**

p-value for Flavor= ???

**FizzSensation:**

p-value for FizzSensation= ???

**PackageDesign:**

p-value for PackageDesign= ???

Eliminate the `FizzSensation` with the highest p-value and run the regression again:

- assign `model3` the result of `lm`, using `OverallSatisfaction ~ Flavor + PackageDesign` as the first argument to `lm` and then `data=df` as the second argument
- call `summary(model1)` to print out the regression model info after creating the model
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Orig:
# CODE 

# Solution:
model3 <- lm(OverallSatisfaction ~ Flavor+PackageDesign, data=df)
summary(model3)
```

FILL IN THE ???? below with the right values from above:

**Test for overall significant of linear relationship:**

overall p-value = ????

**Flavor:**

p-value for Flavor= ???

**PackageDesign:**

p-value for PackageDesign= ???

This is your final model.

**The regression equation is this:**

OverallSatisfaction = ???(Flavor) + ???(PackageDesign) + ???  
    
#### Predictions

Make a dataframe to hold our predictors: 

- rates Flavor 1 and rates PackageDesign 1 
- rates Flavor 2 and rates PackageDesign 3 
- rates Flavor 3 and rates PackageDesign 2 

Do this:  

- assign a vector `Flavor` to hold the three `Flavor` predictor values
- assign a vector `PackageDesign` to hold the three `PackageDesign` predictor values
- create a dataframe with `predictors<-data.frame(Flavor,PackageDesign)` 
- print `predictors` 
```{r include=ex, eval=F}
Flavor<-CODE
PackageDesign<-CODE
predictors <- data.frame(Flavor, PackageDesign)
predictors
```
```{r include=!ex}
# Original:
#Flavor<-CODE
#PackageDesign<-CODE
#predictors <- data.frame(Flavor, PackageDesign)
#predictors

# Solution:
Flavor<-c(1,2,3)
PackageDesign<-c(1,3,2)
predictors <- data.frame(Flavor, PackageDesign)
predictors
```

- make predictions with `predictions<-predict(model3,predictors)` 
- print out the predictions using `print(predictions)`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
# Orig:
# CODE

# Solution:
predictions<-predict(model3, predictors)
print(predictions)
```

Fill in the correct answers below:

- Prediction when rates Flavor 1 and rates PackageDesign 1: ??? 
- Prediction when rates Flavor 2 and rates PackageDesign 3: ??? 
- Prediction when rates Flavor 3 and rates PackageDesign 2: ??? 

