---
title: "More Variables"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r include=F}
ex<-T
```

Lets start by storing a number in a variable. Store 4 in the variable `x` (Hint: Use the assignment operator <-)

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
x<-4
```

Print out the variable `x`:

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
x
```

Set `y` equal to `5*x`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
y<-5*x
```
Now y will have a value after we do this. What is the current value of y? Since the current value of `x` is 4, the value of y should be $5(4)=20$. 

Now print out the value of `y`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
y
```

Variables can be changed as a program proceeds.

Change the value of x to be 7: 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
x<-7
```

One thing you might wonder is that if you change the value of x at some point, does that affect the value of y we defined earlier using x? Let's check:
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
y
```

No. It doesn't. This y still has the same value it had before which is $5(4) = 20$ since at the time we assigned y the x was equal to 4. 
If we want y to update, we would have to assign it again to give it a new value. Go ahead and do that.

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
y<-5*x
```

Now print out the new version of y:

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
y
```
It has the value $5(7) = 35$ now since currently the x is assigned to be 7. 

Next go ahead and set a variable `z` equal to 1.2 and `w` equal to 7 and then print them both out in this block of code

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
z<-1.2
w<-7
z
w
```

Now we change (assign) `z` to be `3*w-5` and print out the new `z`  
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
z<-3*w - 5 
z
```
Since `w` was 7 above, the new value of `z` is $3(7)-5 = 16$

Below we are trying to assign x to be 21 but it does not work. If you try running the code it says that x is still 7.

```{r}
x <= 21
x
```

Provide a correct version below, so that it prints out 21:

```{r include=ex, eval=F}
x <= 21
x
```
```{r include=!ex}
x <- 21
x
```


