---
title: "More Calculator"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

```{r include=F}
ex<-T
```

Calculate `4+5` by replacing the line `CODE HERE` with `4+5` and then execute it by hitting the _Run Cell_ button 

```{r include=ex, eval=F}
CODE HERE
```
```{r include=!ex}
4+5
```

Calculate `4*5`

```{r include=ex, eval=F}
CODE HERE
```
```{r include=!ex}
4*5
```

Calculate `4-5`
```{r include=ex, eval=F}
CODE HERE
```
```{r include=!ex}
4-5
```

Calculate `4/5`
```{r include=ex, eval=F}
CODE HERE
```
```{r include=!ex}
4/5
```

Calculate `4^2`
```{r include=ex, eval=F}
CODE HERE
```
```{r include=!ex}
4^2
```

Check  $4^2=4(4)=16$

Calculate `5^6`
```{r include=ex, eval=F}
CODE HERE
```
```{r include=!ex}
5^6
```

Check  $5^6=(5)(5)(5)(5)(5)(5)=15625$


Calculate `sqrt(36)`
```{r include=ex, eval=F}
CODE HERE
```
```{r include=!ex}
sqrt(36)
```

Check: 
$$ \sqrt{ 36 } = 6 $$

Find `round(2.45)`
```{r include=ex, eval=F}
CODE HERE
```
```{r include=!ex}
round(2.45)
```

Find `ceiling(2.45)`
```{r include=ex, eval=F}
CODE HERE
```
```{r include=!ex}
ceiling(2.45)
```

Find `24%%10`, which is the remainder of $24/10$
```{r include=ex, eval=F}
CODE HERE
```
```{r include=!ex}
24%%10
```

Put parentheses in the expression `4+2*3` so it gives 18. As is, it is 10
```{r include=ex, eval=F}
4+2*3
```
```{r include=!ex}
(4+2)*3
```

Put parentheses in the expression `4*5+3` so it gives 32. As is, it is 23
```{r include=ex, eval=F}
4*5+3
```
```{r include=!ex}
4*(5+3)
```

Put parentheses in the expression `20/4*5` so it gives 1. As is, it is 25
```{r include=ex, eval=F}
20/4*5
```
```{r include=!ex}
20/(4*5)
```

Put parentheses in the expression `2*9/3*2-1` so it gives 2. As is, it is 11 
```{r include=ex, eval=F}
2*9/3*2-1
```
```{r include=!ex}
2*9/(3*2)-1
```

Fix the error below so it works correctly and gives 7
```{r include=ex, eval=F}
sqrt 49
```
```{r include=!ex}
sqrt(49)
```

Fix the error below so it works correctly and gives 8
```{r include=ex, eval=F}
ceil(7.45)
```
```{r include=!ex}
ceiling(7.45) 
```

Fix the error below so it works correctly and gives 7 
```{r include=ex, eval=F}
flooring(7.45)
```
```{r include=!ex}
floor(7.45) 
```

