---
params:
  a:
    input: numeric
    label: a
    max: 100
    min: 0
    step: 1
    value: 21
  b:
    input: numeric
    label: b
    max: 100
    min: 0
    step: 1
    value: 28
  mu:
    input: numeric
    label: mu
    max: 80
    min: 50
    step: 1
    value: 24
  sigma:
    input: numeric
    label: sigma
    max: 10
    min: 0
    step: 1
    value: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
dnorm_limit <- function(x) {
 y <- dnorm(x)
 y[x < -1.2 | x > 2.1] <- NA
 return(y)
}
```

## Area under normal curve between two values

We are going to find the area between the two x-values by using the standard normal (z) table:

For the left endpoint (x=a) the z-value is:

$$
`r {
    x<-params$a; 
    mu<-params$mu; 
    numer<-(x-mu); 
    sigma<-params$sigma; 
    z<-(x-mu)/sigma
    sprintf("z=\\frac{x-\\mu}{\\sigma}=\\frac{%s-%s}{%s}=\\frac{%s}{%s}=%s",
                                                x,mu,sigma,numer,sigma,z)
   }`
$$

For the right endpoint (x=b) the z-value is:

$$
`r {
    x<-params$b; 
    mu<-params$mu; 
    numer<-(x-mu); 
    sigma<-params$sigma; 
    z<-(x-mu)/sigma
    sprintf("z=\\frac{x-\\mu}{\\sigma}=\\frac{%s-%s}{%s}=\\frac{%s}{%s}=%s",
                                                x,mu,sigma,numer,sigma,z)
   }`
$$

Here is a picture of the area that we want.

```{r area, echo=FALSE}
#change dev to svg if need to
#dat <- data.frame(x=c(-3.5, 3.5))
#ggplot(dat, aes(x=x)) +
#stat_function(fun=dnorm_limit, geom="area", fill="blue", alpha=0.5) +
#stat_function(fun=dnorm) +
#labs(x = "z", y = "") +
#geom_hline(yintercept=0) +
#scale_x_continuous(breaks = seq(-3, 3, by = 1.0)) +
#scale_y_continuous(breaks = seq(0, .4, by = 0.2)) +
#annotate("text", x = -1.2, y = -0.01, label = "hi") +
#annotate("text", x = 2.1, y = -0.01, label = "bye")
```


* Parameters
    * a is `r params$a` and the fraction is \(\frac{`r params$a`}{4}\)
    * b is $\frac{3}{4}$
* another bullet point 

# Parameter a is `r params$a` and b is `r params$b` 
