---
title: "Regression Tree: Predicting Demand from Radio and Email"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---
```{r, include=FALSE}
assignment<-T
```

```{r echo=T, results='hide', message=F, warning=F}
if(!require("rpart")) install.packages("rpart")
if(!require("rpart.plot")) install.packages("rpart.plot")
if(!require("Metrics")) install.packages("Metrics")
library("rpart")
library("rpart.plot")
library("Metrics")
```

We have training data for 13 weeks.

- `demand` is the demand for the week
- `radio` (yes or no), is whether we ran radio ads that week
- `email` (yes or no) is whether we emailed potential customers that week 

## Training Data

Lets read in the training data:

```{r}
url<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vSi4B1BrrvBiibT9af_txYMmTNxPJ7Q7Y9502MFjeYUpMXBiiIT3Mlv28h2hPa69bmAuzIc95PuNvN-/pub?gid=1414619388&single=true&output=csv"
train<-read.csv(url, stringsAsFactors=TRUE)
```
- print out info about the `train` dataset using `str`:
```{r include=assignment, eval=FALSE}
CODE
```
```{r include=!assignment}
str(train)
```

- And now print out the training set using `print`:
```{r include=assignment, eval=FALSE}
CODE
```
```{r include=!assignment}
print(train)
```

## Testing Data

```{r}
url<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vSi4B1BrrvBiibT9af_txYMmTNxPJ7Q7Y9502MFjeYUpMXBiiIT3Mlv28h2hPa69bmAuzIc95PuNvN-/pub?gid=0&single=true&output=csv"
test<-read.csv(url, stringsAsFactors=TRUE)
```

- print out info about the `test` dataset using `str`:
```{r include=assignment, eval=FALSE}
CODE
```
```{r include=!assignment}
str(test)
```

- And now print out the test set using `print`:
```{r include=assignment, eval=FALSE}
CODE
```
```{r include=!assignment}
print(test)
```


## Model 1 - use `radio` only to predict `demand` 

- sort the data frame using `radio`
```{r}
print(train[order(train$radio),])
```

Now lets make model 1 using just one predictor `radio` and one node to predict `demand`:

- replace CODE below with the correct model to predict `demand` from `radio` only
```{r include=assignment, eval=FALSE}
control <- rpart.control(minbucket=1, maxdepth=1)
model <- rpart(CODE, data=train, method="anova", control=control)
rpart.plot(model, type=4, extra=101)
```
```{r include=!assignment}
control <- rpart.control(minbucket=1, maxdepth=1)
model <- rpart(demand~radio, data=train, method="anova", control=control)
rpart.plot(model, type=4, extra=101)
```

### Fill in the following information for this model:

Prediction if there is there is no radio promotion: ???

Prediction if there is radio promotion: ???     

These values come from taking averages over radio `no` and radio `yes`

- Now we are ready to do some predictions using `predictions <- predict(model, newdata = test)`:
```{r include=assignment, eval=FALSE}
predictions <- CODE 
```
```{r include=!assignment}
predictions <- predict(model, newdata = test)
```

- Compute the MAE, MAPE and RMSE for this model using `mae(actuals,predictions)`, `mape(actuals, predictions)` and `rmse(actuals, predictions)`
```{r include=assignment, eval=FALSE}
actuals <- test$demand
mae(CODE)
mape(CODE)
rmse(CODE)
```
```{r include=!assignment}
actuals <- test$demand
mae(actuals, predictions)
mape(actuals, predictions)
rmse(actuals, predictions)
```

## Model 2 - use `radio` and `email` to predict `demand` 

Now lets do model 2 using both `radio` and `email` and one node to predict `demand`:

- replace CODE below with the correct model to predict `demand` from `radio`and `email` 
```{r include=assignment, eval=FALSE}
control <- rpart.control(minbucket=1)
model <- rpart(CODE, data=train, method="anova", control=control)
rpart.plot(model, type=4, extra=101)
```
```{r include=!assignment}
control <- rpart.control(minbucket=1)
model <- rpart(demand~email+radio, data=train, method="anova", control=control)
rpart.plot(model, type=4, extra=101)
```

### Fill in the following information for this model:

Prediction if there is there is no email promotion and there is radio promotion: ???

Prediction if there is there is email promotion and there is radio promotion ??? 

- make some predictions using `predictions <- predict(model, newdata = test)`
```{r include=assignment, eval=FALSE}
predictions <- CODE 
```
```{r include=!assignment}
predictions <- predict(model, newdata = test)
```

- Compute the MAE, MAPE and RMSE for this model using `mae(actuals,predictions)`, `mape(actuals, predictions)` and `rmse(actuals, predictions)`
```{r include=assignment, eval=FALSE}
actuals <- test$demand
mae(CODE)
mape(CODE)
rmse(CODE)
```
```{r include=!assignment}
actuals <- test$demand
mae(actuals, predictions)
mape(actuals, predictions)
rmse(actuals, predictions)
```

### Which Model is Better?

Which model was better, model1 or model2  ???
