---
title: "Promotion Forecasting"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r eval=FALSE}
install.packages("RCurl")
```

Then make sure it is loaded:
```{r}
library("RCurl")
```

We use the getURL and read the csv as a textstring:
```{r}
url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vS2Z4rEXAoVmrunY3BLJ5AX-ZH76U8bHpCCOu8mzziWK1X6WnJJiC2RmrWrLffGUxo9dCZD0HW1n15T/pub?gid=1471239210&single=true&output=csv"
textString<-getURL(url)
df<-read.csv(text=textString)
```

Here is the structure of the dataframe

```{r}
str(df)
```

```{r}
df
```

```{r}
plot(df$week, df$demand, main="Demand for 26 Weeks", xlab="Week", ylab="Demand", type="l")
points(df$week, df$demand, pch=19)
```

```{r}
options("scipen"=100, "digits"=4)
model <- lm(demand~p114+p101+specialEvents, df)
summary(model)
```

This means that both the markdowns and the holiday events have a significant linear relationship with demand. 

In particular:

* when the 15% markdown is run it accounts for roughly an increase in 86 units of demand. 
* when the 25% markdown is run it accounts for roughly an increase in 111 units of demand. 
* special holiday event promotions accounts for roughly an increase in 69 units of demand. 

What about a demand curve? Can we make one of these:
```{r}
plot(df$price, df$demand, main="Demand Curve", xlab="Price", ylab="Demand", type="p", pch=19)
model2 <- lm(demand~price, df)
abline(reg=model2)
```

Here is the summary of the regression of demand and price.

```{r}
summary(model2)
```

We could use this to do some price optimization and elasticity analysis. 
