---
title: "Predicting Demand from Radio and Email Campaigns"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---
```{r, include=FALSE}
assignment<-TRUE
```

```{r echo=T, results='hide', message=F, warning=F}
options("scipen"=100, "digits"=4)
if(!require("readr")) install.packages("readr")
if(!require("rpart")) install.packages("rpart")
if(!require("rpart.plot")) install.packages("rpart.plot")
if(!require("Metrics")) install.packages("Metrics")
library("readr")
library("rpart")
library("rpart.plot")
library("Metrics")
```

We have data for 14 weeks.

- `demand` is the demand for the week
- `radio` (yes or no), is whether we ran radio ads that week
- `email` (yes or no) is whether we emailed potential customers that week 

Lets read in the training data:

```{r}
trainurl<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vSi4B1BrrvBiibT9af_txYMmTNxPJ7Q7Y9502MFjeYUpMXBiiIT3Mlv28h2hPa69bmAuzIc95PuNvN-/pub?gid=1414619388&single=true&output=csv"
traindf<-read.csv(trainurl, stringsAsFactors=TRUE)
str(traindf)
```
Let's print out the training set to make sure it looks like what we expect:

```{r}
print(traindf)
```

## Model1 - use `radio` only to predict `demand` 

Now lets make model1 using just one predictor `radio` and one node to predict `demand`:

```{r include=assignment, eval=FALSE}
control <- rpart.control(minbucket=1, maxdepth=1)
model1<- PUT CODE HERE
rpart.plot(model1, type=4, extra=101)
```
```{r include=!assignment}
control <- rpart.control(minbucket=1, maxdepth=1)
model1 <- rpart(demand~radio, data=traindf, method="anova", control=control)
rpart.plot(model1, type=4, extra=101)
```

### Fill in the following infomation for this model:

Prediction if there is there is no radio promotion:     

PUT ANSWER HERE

Prediction if there is radio promition:     

PUT ANSWER HERE

```{r}
testurl<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vSi4B1BrrvBiibT9af_txYMmTNxPJ7Q7Y9502MFjeYUpMXBiiIT3Mlv28h2hPa69bmAuzIc95PuNvN-/pub?gid=0&single=true&output=csv"
testdf<-read.csv(testurl, stringsAsFactors=TRUE)
```

And now print out the test set:

```{r}
print(testdf)
```

Now we are ready to do some predictions for `model1` using the test dataframe:

```{r include=assignment, eval=FALSE}
predictions <- PUT CODE HERE 
```
```{r include=!assignment}
predictions <- predict(model1, newdata = testdf)
```

Compute the MAE, MAPE and RMSE for model1:
(use `actuals` and `predictions`)

```{r include=assignment, eval=FALSE}
actuals <- testdf$demand
mae(PUT CODE HERE)
mape(PUT CODE HERE)
rmse(PUT CODE HERE)
```
```{r include=!assignment}
actuals <- testdf$demand
mae(actuals, predictions)
mape(actuals, predictions)
rmse(actuals, predictions)
```

## Model2 - use `radio` and `email` to predict `demand` 

Now lets do model2 using both `radio` and `email` and one node to predict `demand`:

```{r include=assignment, eval=FALSE}
control <- rpart.control(minbucket=1)
model2 <- PUT CODE HERE 
rpart.plot(model2, type=4, extra=101)
```
```{r include=!assignment}
control <- rpart.control(minbucket=1)
model2 <- rpart(demand~email+radio, data=traindf, method="anova", control=control)
rpart.plot(model2, type=4, extra=101)
```

### Fill in the following infomation for this model:

Prediction if there is there is no email promotion and there is radio promotion:     

PUT ANSWER HERE

Prediction if there is there is email promotion and there is radio promotion:     

PUT ANSWER HERE

Now read in the test dataframe

```{r}
testurl<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vSi4B1BrrvBiibT9af_txYMmTNxPJ7Q7Y9502MFjeYUpMXBiiIT3Mlv28h2hPa69bmAuzIc95PuNvN-/pub?gid=0&single=true&output=csv"
testdf<-read.csv(testurl, stringsAsFactors=TRUE)
```

And now print out the test set:

```{r}
print(testdf)
```

Now we are ready to do some predictions using the test dataframe:

```{r include=assignment, eval=FALSE}
predictions <- PUT CODE HERE 
```
```{r include=!assignment}
predictions <- predict(model2, newdata = testdf)
```

```{r include=assignment, eval=FALSE}
actuals <- testdf$demand
mae(PUT CODE HERE)
mape(PUT CODE HERE)
rmse(PUT CODE HERE)
```
```{r include=!assignment}
actuals <- testdf$demand
mae(actuals, predictions)
mape(actuals, predictions)
rmse(actuals, predictions)
```

Which model was better, `model1` or `model2` and why?
