---
title: "Purchased"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r echo=T, results='hide', message=F, warning=F}
options("scipen"=100, "digits"=4)

if(!require("rpart")) install.packages("rpart")
if(!require("rpart.plot")) install.packages("rpart.plot")
if(!require("Metrics")) install.packages("Metrics")

library("rpart")
library("rpart.plot")
library("Metrics")
```

## The Training Data 

So here is the data we have, this will be our training data:

- `Purchased` is our result or outcome
- `Salary`, `Age` are the predictors

This data is about what kinds of customers responded to an email add offering a special deal on a product. Were they high salary or low salary and what about their age? We would like to know if `Salary` and `Age` of the customer help us predict whether they bought an item based on the offer they got.

Here is our training set:

| Salary | Age | Purchased |
|--------|-----|-----------|
| 53700  | 41  | no        |
| 65300  | 37  | no        |
| 48900  | 45  | yes       |
| 64800  | 49  | yes       |
| 69200  | 30  | yes       |
| 55900  | 57  | yes       |
| 48600  | 26  | no        |
| 72000  | 60  | yes       |
| 45300  | 34  | no        |
| 69000  | 32  | yes       |
| 73200  | 52  | yes       |

Lets read it in:

```{r}
url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTx21HIv4xKL2c94OLQzMiNPmv5YXw-vAy3dRBL0gnknSMKMK4Ur_4nYGGyDtvS20iU3_r-_zZfQQmj/pub?gid=0&single=true&output=csv"
train<-read.csv(url)
str(train)
```

## The Testing Data 

Here we read the test set:

| Salary | Age | Purchased |
|--------|-----|-----------|
| 53900  | 45  | yes       |
| 64800  | 49  | yes       |
| 50000  | 32  | no        |
| 55900  | 57  | yes       |
| 55600  | 29  | no        |
| 60000  | 25  | no        |

```{r}
#read the testing set
url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTx21HIv4xKL2c94OLQzMiNPmv5YXw-vAy3dRBL0gnknSMKMK4Ur_4nYGGyDtvS20iU3_r-_zZfQQmj/pub?gid=572053114&single=true&output=csv"
test<-read.csv(url)
str(test)
```

### Model Purchased~Salary

#### Model With Training Data

We are going to model this situation with a decision tree. We will start by just trying to use `Salary` to predict the result:

Lets look at the data sorted by Salary:

```{r}
print(train[order(train$Salary),])
```

It appears that mostly those with higher salary purchased. 

Lets look at the split on `Salary`

```{r}
control = rpart.control(minsplit=1,maxdepth=1)
model <- rpart(Purchased~Salary, data=train, method="class", control = control)
rpart.plot(model, type=4, extra=101, digits=-2)
```

#### Test With Testing Data

Here are the predictions for our test data:

```{r}
pred <- predict(model, newdata = test, type = 'class')
compare <- data.frame(actual=test, predictions=pred)
print(compare)
```

Here is the confusion matrix:

```{r}
table(test$Purchased, pred)
```

Here is the accuracy:

```{r}
accuracy(test$Purchased, pred)
```

### Model Purchased~Age

#### Model With Training Data

Lets look at the data sorted by Age:

```{r}
print(train[order(train$Age),])
```

It appears that mostly older purchased 

Lets look at the split on `Age`

```{r}
control = rpart.control(minsplit=1,maxdepth=1)
model <- rpart(Purchased~Age, data=train, method="class", control = control)
rpart.plot(model, type=4, extra=101, digits=-2)

```

#### Test With Testing Data

Here are the predictions for our test data:

```{r}
pred <- predict(model, newdata = test, type = 'class')
compare <- data.frame(actual=test, predictions=pred)
print(compare)
```

Here is the confusion matrix:

```{r}
table(test$Purchased, pred)
```

Here is the accuracy:

```{r}
accuracy(test$Purchased, pred)
```

### Model Purchased~Salary grown out 

#### Model With Training Data

How about if we grow the `Salary` tree even more?

```{r}
control = rpart.control(minsplit=1,maxdepth=3, cp=-1)
model <- rpart(Purchased~Salary, data=train, method="class", control = control)
rpart.plot(model, type=4, extra=101, digits=-2)
```

#### Test With Testing Data

Here are the predictions for our test data:

```{r}
pred <- predict(model, newdata = test, type = 'class')
compare <- data.frame(actual=test, predictions=pred)
print(compare)
```

Here is the confusion matrix:

```{r}
table(test$Purchased, pred)
```

Here is the accuracy:

```{r}
accuracy(test$Purchased, pred)
```

### Model Purchased~Salary grown Full Tree 

#### Model With Training Data

How about all out with `Salary`:

```{r}
control = rpart.control(minsplit=1)
model <- rpart(Purchased~Salary, data=train, method="class", control = control)
rpart.plot(model, type=4, extra=101, digits=-2)
```

#### Test With Testing Data

Here are the predictions for our test data:

```{r}
pred <- predict(model, newdata = test, type = 'class')
compare <- data.frame(actual=test, predictions=pred)
print(compare)
```

Here is the confusion matrix:

```{r}
table(test$Purchased, pred)
```

Here is the accuracy:

```{r}
accuracy(test$Purchased, pred)
```

### Model 6 Purchased~Salary+Age

#### Model With Training Data

Finally lets build a model that uses both Salary and Age:

```{r}
control = rpart.control(minsplit=1)
model <- rpart(Purchased~Salary+Age, data=train, method="class", control = control)
rpart.plot(model, type=4, extra=101, digits=-2)
```

#### Test With Testing Data

Here are the predictions for our test data:

```{r}
pred <- predict(model, newdata = test, type = 'class')
compare <- data.frame(actual=test, predictions=pred)
print(compare)
```

Here is the confusion matrix:

```{r}
table(test$Purchased, pred)
```

Here is the accuracy:

```{r}
accuracy(test$Purchased, pred)
```
