---
title: "Purchased"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

```{r echo=T, results='hide', message=F, warning=F}
options("scipen"=100, "digits"=4)
if(!require("readr")) install.packages("readr")
if(!require("rpart")) install.packages("rpart")
if(!require("rpart.plot")) install.packages("rpart.plot")
if(!require("Metrics")) install.packages("Metrics")
library("readr")
library("rpart")
library("rpart.plot")
library("Metrics")
```

## Building the Decision Tree using the training set

So here is the data we have, this will be our training data:

- `Purchased` is our result or outcome
- `Salary`, `Age` are the predictors

This data is about what kinds of customers responded to an email add offering a special deal on a product. Were they high salary or low salary and what about their age? We would like to know if `Salary` and `Age` of the customer help us predict whether they bought an item based on the offer they got.

Here is our training set:

| Salary | Age | Purchased |
|--------|-----|-----------|
| 53700  | 41  | no        |
| 65300  | 37  | no        |
| 48900  | 45  | yes       |
| 64800  | 49  | yes       |
| 69200  | 30  | yes       |
| 55900  | 57  | yes       |
| 48600  | 26  | no        |
| 72000  | 60  | yes       |
| 45300  | 34  | no        |
| 69000  | 32  | yes       |
| 73200  | 52  | yes       |

Lets read it in:

```{r}
trainurl<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTx21HIv4xKL2c94OLQzMiNPmv5YXw-vAy3dRBL0gnknSMKMK4Ur_4nYGGyDtvS20iU3_r-_zZfQQmj/pub?gid=0&single=true&output=csv"
traindf<-read.csv(trainurl, stringsAsFactors=TRUE)
str(traindf)
```

```{r, eval=F, include=F}
read.md <- function(file = clipr::read_clip(),
                    delim = '|',
                    stringsAsFactors = FALSE,
                    strip.white = TRUE,
                    ...){
    if (length(file) > 1) {
        lines <- file
    } else if (grepl('\n', file)) {
        con <- textConnection(file)
        lines <- readLines(con)
        close(con)
    } else {
        lines <- readLines(file)
    }
    lines <- lines[!grepl('^[\\:\\s\\+\\-\\=\\_\\|]*$', lines, perl = TRUE)]
    lines <- gsub('(^\\s*?\\|)|(\\|\\s*?$)', '', lines)
    utils::read.delim(text = paste(lines, collapse = '\n'), sep = delim,
                      stringsAsFactors = stringsAsFactors,
                      strip.white = strip.white, ...)
train<-'
'
traindf<-read.md(train, stringsAsFactors=TRUE)
str(traindf)

test<-'
'
testdf<-read.md(test, stringsAsFactors=TRUE) 
str(testdf)
```

We are going to model this situation with a decision tree. We will start by just trying to use `Salary` to predict the result:

```{r}
control = rpart.control(minsplit=1,maxdepth=1)
model1 <- rpart(Purchased~Salary, data=traindf, method="class", control = control)
rpart.plot(model1, type=4, extra=101, digits=-2)
```

What about if we use `Age` to predict the result:

```{r}
control = rpart.control(minsplit=1,maxdepth=1)
model2 <- rpart(Purchased~Age, data=traindf, method="class", control = control)
rpart.plot(model2, type=4, extra=101, digits=-2)
```

We about if we use `Salary` but let the tree grow a little:

```{r}
control = rpart.control(minsplit=1,maxdepth=2, cp=-1)
model3 <- rpart(Purchased~Salary, data=traindf, method="class", control = control)
rpart.plot(model3, type=4, extra=101, digits=-2)
```

How about if we grow the `Salary` tree even more:

```{r}
control = rpart.control(minsplit=1,maxdepth=3, cp=-1)
model4 <- rpart(Purchased~Salary, data=traindf, method="class", control = control)
rpart.plot(model4, type=4, extra=101, digits=-2)
```

How about all out with `Salary`:

```{r}
control = rpart.control(minsplit=1)
model5 <- rpart(Purchased~Salary, data=traindf, method="class", control = control)
rpart.plot(model5, type=4, extra=101, digits=-2)
```

## Testing the Decision Tree model using the testing set

Now lets doe some predictions using the test dataframe:

Here we read the test set:

| Salary | Age | Purchased |
|--------|-----|-----------|
| 53900  | 45  | yes       |
| 64800  | 49  | yes       |
| 50000  | 32  | no        |
| 55900  | 57  | yes       |
| 55600  | 29  | no        |
| 60000  | 25  | no        |

```{r}
#read the testing set
testurl<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTx21HIv4xKL2c94OLQzMiNPmv5YXw-vAy3dRBL0gnknSMKMK4Ur_4nYGGyDtvS20iU3_r-_zZfQQmj/pub?gid=572053114&single=true&output=csv"
testdf<-read.csv(testurl, stringsAsFactors=TRUE)
str(testdf)
```

Lets test our last model (model5) and see how well these predictions agree with the actual in the test set. Here is the "accuracy" for model5:

```{r}
pred <- predict(model5, newdata = testdf, type = 'class')
accuracy(testdf$Purchased, pred)
```

Lets make a data frame that shows the prediction and the actuals for model5: 

```{r}
comparedf <- data.frame(actual=testdf$Purchased, predictions=pred)
print(comparedf)
```

Lets test model4 for its accuracy: 

```{r}
pred <- predict(model4, newdata = testdf, type = 'class')
accuracy(testdf$Purchased, pred)
```

And model3:

```{r}
pred <- predict(model3, newdata = testdf, type = 'class')
accuracy(testdf$Purchased, pred)
```

And model2:

```{r}
pred <- predict(model2, newdata = testdf, type = 'class')
accuracy(testdf$Purchased, pred)
```

Finally lets build a model that uses both Salary and Age:

```{r}
control = rpart.control(minsplit=1)
model6 <- rpart(Purchased~Salary+Age, data=traindf, method="class", control = control)
rpart.plot(model6, type=4, extra=101, digits=-2)
```

Lets check the accuracy of this model that uses both variables:

```{r}
pred <- predict(model6, newdata = testdf, type = 'class')
accuracy(testdf$Purchased, pred)
```

Lets make a data frame that shows the prediction and the actuals for this model6: 

```{r}
comparedf <- data.frame(actual=testdf$Purchased, predictions=pred)
print(comparedf)
```
