---
title: "Purchased Knn"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r echo=T, results='hide', message=F, warning=F}
options("scipen"=100, "digits"=4)
if(!require("readr")) install.packages("readr")
if(!require("knitr")) install.packages("knitr")
if(!require("Metrics")) install.packages("Metrics")
if(!require("class")) install.packages("class")
library("readr")
library("Metrics")
library("class")
library("knitr")
knitr::opts_chunk$set(fig.width=5, fig.height=5)
normalize <- function(x) {
    return ( (x-min(x))/(max(x)-min(x)) )
}
```

## Using Knn to decide if customer will Purchase based on email ad campaign 

So here is the data we have, this will be our training data:

- `Purchased` is our result or outcome
- `Salary`, `Age` are the predictors

This data is about what kinds of customers responded to an email ad offering a special deal on a product. Were they high salary or low salary and what about their age? We would like to know if `Salary` and `Age` of the customer can predict whether they bought an item based on the offer they received.

Here is our training set:

| Salary | Age | Purchased |
|--------|-----|-----------|
| 53700  | 41  | no        |
| 65300  | 37  | no        |
| 48900  | 45  | yes       |
| 64800  | 49  | yes       |
| 69200  | 30  | yes       |
| 55900  | 57  | yes       |
| 48600  | 26  | no        |
| 72000  | 60  | yes       |
| 45300  | 34  | no        |
| 69000  | 32  | yes       |
| 73200  | 52  | yes       |

Lets read it in:

```{r}
trainurl<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTx21HIv4xKL2c94OLQzMiNPmv5YXw-vAy3dRBL0gnknSMKMK4Ur_4nYGGyDtvS20iU3_r-_zZfQQmj/pub?gid=0&single=true&output=csv"
traindf<-read.csv(trainurl, stringsAsFactors=TRUE)
str(traindf)
```

Lets print it out to make sure it looks okay:

```{r}
print(traindf)
```

Lets take a look at a graph of the two predictors:

```{r}
plot(traindf$Salary, traindf$Age, col=traindf$Purchased, 
     pch=19,
     xlab="Salary",
     ylab="Age",
     xlim=c(40000,80000), ylim=c(20,70))
```

We are going to model this situation using Knn (K nearest neighbors):

Knn needs both the training and the test set passed to it:

Here is our test set:

| Salary | Age | Purchased |
|--------|-----|-----------|
| 53900  | 45  | yes       |
| 64800  | 49  | yes       |
| 50000  | 32  | no        |
| 55900  | 57  | yes       |
| 55600  | 29  | no        |
| 60000  | 25  | yes       |

Lets read it in:

```{r}
#read the testing set
testurl<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTx21HIv4xKL2c94OLQzMiNPmv5YXw-vAy3dRBL0gnknSMKMK4Ur_4nYGGyDtvS20iU3_r-_zZfQQmj/pub?gid=572053114&single=true&output=csv"
testdf<-read.csv(testurl, stringsAsFactors=TRUE)
str(testdf)
```

Lets print it out:

```{r}
print(testdf)
```

Now lets extract the last column of the training dataset since we need it as the 'cl' argument in the knn function. We also remove the `Shirt` column from the data frames since knn expects the dataframes to have no result columns. 

```{r}
train_target <- traindf$Purchased 
traindf$Purchased <- NULL

print(traindf)

test_target <- testdf$Purchased
testdf$Purchased <- NULL
```

Now before we run the Knn algorithm, we need to normalize (or rescale) the predictors:

```{r}
traindf_n <- as.data.frame(lapply(traindf, normalize))
testdf_n <- as.data.frame(lapply(testdf, normalize))
print(traindf_n)
```

Notice how the predictors are all normalized into the range 0.0 to 1.0

```{r}
set.seed(1234)
prediction<-knn(traindf_n,testdf_n, cl=train_target, k=4)
str(prediction)
print(prediction)
```

We put the actuals and predictions back into the testdf so we can check the accuracy:

```{r}
testdf$Purchased <- test_target
testdf$Prediction <- prediction
print(testdf)
```

```{r}
table(prediction=prediction,actual=test_target)
accuracy(test_target, prediction)
```

```{r}
salary<-normalize(testdf$Salary)
age<-normalize(testdf$Age)
plot(traindf_n$Salary, 
     traindf_n$Age, 
     col=train_target, 
     pch=19, 
     xlab="Salary",
     ylab="Age")
points(salary[1], 
       age[1], 
       pch=19, 
       col="blue")
```

```{r}
salary<-normalize(testdf$Salary)
age<-normalize(testdf$Age)
plot(traindf_n$Salary, 
     traindf_n$Age, 
     col=train_target, 
     pch=19, 
     xlab="Salary",
     ylab="Age")
points(salary[2], 
       age[2], 
       pch=19, 
       col="blue")
```
