---
title: "R Basics and DataFrames"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r, include=FALSE}
solution<-FALSE
```

- Create a variable `z` that has value 32
```{r, eval=FALSE, include=!solution}
z <- CODE 
```
```{r, include=solution}
z <- 32
```

- Create a variable `w` that is equal to `z/3`
```{r, eval=FALSE, include=!solution}
w <- CODE
```
```{r, include=solution}
w <- z/3 
```

- Define a character vector `a` that has these strings on it "Hello", "Goodbye", "Goodnight", "Bye":
```{r, eval=FALSE, include=!solution}
a<-CODE
```
```{r, include=solution}
a<- c("Hello", "Goodbye", "Goodnight", "Bye")
```

Define a vector variable `q` that has 3,-3,2,-1,0,-4,-6,3,-7,4,2,3,-2,-4,4 on it. 

```{r, eval=FALSE, include=!solution}
q<-CODE
```
```{r, include=solution}
q<- c(3,-3,2,-1,0,-4,-6,3,-7,4,2,3,-2,-4,4) 
```

Next create a dataframe for this data:

|  Name  |  GPA | Major |  Phone    |
|:------:|:----:|:---:|:------------:|
| Alexa |  3.7 | FBM | 212 398 2375 |
| Tanya |  3.6 | AMC | 212 323 3040 |
| Hubert |  3.4 | FBM | 718 232 9392 |

 - create a dataframe for this data
```{r, eval=FALSE, include=!solution}
Name<-CODE
GPA<-CODE
Major<-CODE
Phone<-CODE
df <- data.frame(CODE,CODE,CODE,CODE) 
```
```{r, include=solution}
Name<-c("Alexa", "Tanya", "Hubert")
GPA<-c(3.7, 3.6, 3.4)
Major<-c("FBM", "AMC", "FBM")
Phone<-c("212 398 2375", "212 323 3040", "718 232 9392")
df <- data.frame(Name,GPA,Major,Phone) 
```

- Print out the structure of your data frame using `str`
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
str(df)
```

- Print out just the GPA column using $ sign: (Replace CODE below with the right column name for this. 
```{r, eval=FALSE, include=!solution}
df$CODE
```
```{r, include=solution}
df$GPA
```

- Now print out the first few lines of the data frame using `head`
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
head(df)
```

- Use `summary(df)` to print out a summary of the data frame data:
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
summary(df)
```

- Delete the column "Major" from the data frame:
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
df$Major <- NULL
```

- Print out the structure of your data frame showing the column above removed: 

```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
str(df)
```

Finally add a column called "ID" 
Your data frame will look like this after doing this:  

|  Name  |  GPA |  Phone       | ID  |
|:------:|:----:|:------------:|:---:|
| Alexa |  3.7 | 212 398 2375 | 1001 |
| Tanya |  3.6 | 212 323 3040 | 1002 |
| Hubert |  3.4 | 718 232 9392 | 1003 |

- add a column called "ID" 
```{r, eval=FALSE, include=!solution}
df$ID <- CODE 
```
```{r, include=solution}
df$ID <- c(1001,1002,1003)
```

- Print out the structure of the new data frame using `str`:
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
str(df)
```

- Change Tanyas GPA in the dataframe to be `3.98`
```{r, eval=FALSE, include=!solution}
df[2,2] <- CODE 
```
```{r, include=solution}
df[2,2] <- 3.98
```

- Print out the data frame using `head` to make sure her GPA is changed:
```{r, eval=FALSE, include=!solution}
CODE
```
```{r, include=solution}
head(df)
```
