
# Elasticity 

This notebook is from the following, and is just a simplified version of it:
[Price Elasticity with R](http://www.salemmarafi.com/code/price-elasticity-with-r)   

Also see here: [Pricing Analysis Example](https://rstudio-pubs-static.s3.amazonaws.com/185880_f9e3e3ee84314609b531524dfa3f4f1b.html) 

First make sure RCurl is installed.

```{r eval=FALSE}
install.packages("RCurl")
```

Then make sure it is loaded:

```{r}
library("RCurl")
```

We use the getURL function from the RCurl package to load the data from the website. It is returned to us as a text string. 

```{r}
#textString<-getURL("http://www.salemmarafi.com/wp-content/uploads/2014/06/supermarket.csv")
textString<-getURL("https://raw.githubusercontent.com/PacktPublishing/Jupyter-for-Data-Science/master/Chapter01/grapeJuice.csv")
df<-read.csv(text=textString)
```

Here is the structure of the data set.

```{r}
str(df)
```

Here are the first few terms 

```{r}
head(df, 10)
```

Lets look at the  

```{r}
par(mfrow=c(1,2))
boxplot(df$sales,main="Boxplot for sales data", xlab="grape sales")
hist(df$sales,main='histogram plot for sales data',xlab='grape sales',prob=T)
```
