---
title: "Restaurant"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r, include=FALSE}
blanks<-TRUE
solution<-FALSE
```
```{r}
options("scipen"=100, "digits"=4)
if(!require("readr")) install.packages("readr")
if(!require("rpart")) install.packages("rpart")
if(!require("rpart.plot")) install.packages("rpart.plot")
library("readr")
library("rpart")
library("rpart.plot")
```

| Alternate | Bar | Fri/Sat | Hungry | Patrons | Price | Raining | Reservation | Type | WaitEstimate | WillWait |
|-----------|-----|---------|--------|---------|-----------|---------|-------------|---------|--------------|----------|
| Yes | No | No | Yes | Some | Expensive | No | Yes | French | 0-10 | Yes |
| Yes | No | No | Yes | Full | Cheap | No | No | Thai | 30-60 | No |
| No | Yes | No | No | Some | Cheap | No | No | Burger | 0-10 | Yes |
| Yes | No | Yes | Yes | Full | Cheap | No | No | Thai | 10-30 | Yes |
| Yes | No | Yes | No | Full | Expensive | No | Yes | French | >60 | No |
| No | Yes | No | Yes | Some | Moderate | Yes | Yes | Italian | 0-10 | Yes |
| No | Yes | No | No | None | Cheap | Yes | No | Burger | 0-10 | No |
| No | No | No | Yes | Some | Moderate | Yes | Yes | Thai | 0-10 | Yes |
| No | Yes | Yes | No | Full | Cheap | Yes | No | Burger | >60 | No |
| Yes | Yes | Yes | Yes | Full | Expensive | No | Yes | Italian | 10-30 | No |
| No | No | No | No | None | Cheap | No | No | Thai | 0-10 | No |
| Yes | Yes | Yes | Yes | Full | Cheap | No | No | Burger | 30-60 | Yes |

```{r}
url<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vQvQ1hQJoj_3BmOV3uLWcDzwIw3GFhkS84NePBS57lnCmXSN86KU8kn4aQUE9rGsxJPMi32S55JBl9w/pub?gid=0&single=true&output=csv"
traindf<-read.csv(url, stringsAsFactor=TRUE)
```

Now let's print out the training set to make sure we read it correctly:

```{r}
print(traindf)
```

Create models for the following individual predictors with maxdepth=1.

```{r, eval=FALSE, include=blanks}
PUT CODE HERE to create a model  WillWait~Price (use maxdepth = 1) 
```
```{r, include=solution}
control = rpart.control(minsplit=1, maxdepth=1)
model <- rpart(WillWait~Price, data=traindf, method="class", control = control)
rpart.plot(model, type=4, extra = 1, digits=-2)
```

```{r, eval=FALSE, include=blanks}
PUT CODE HERE to create a model  WillWait~Patrons(use maxdepth = 1) 
```
```{r, include=solution}
control = rpart.control(minsplit=1, maxdepth=1)
model <- rpart(WillWait~Patrons, data=traindf, method="class", control = control)
rpart.plot(model, type=4, extra = 1, digits=-2)
```

Which of the above models is better?

Finally here is a model using all the variables
```{r}
control = rpart.control(minsplit=1)
model <- rpart(WillWait~., data=traindf, method="class", control = control)
rpart.plot(model, type=4, extra = 1, digits=-2)
```

Lets read in the testing data set:

```{r, eval=TRUE}
testurl<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vQvQ1hQJoj_3BmOV3uLWcDzwIw3GFhkS84NePBS57lnCmXSN86KU8kn4aQUE9rGsxJPMi32S55JBl9w/pub?gid=289547774&single=true&output=csv"
testdf<-read.csv(testurl, stringsAsFactors=TRUE)
str(testdf)
```
Do a prediction for the testing data set using the model above:

```{r, eval=TRUE}
pred <- predict(model, newdata = testdf, type = 'class')
```

Lets print out the predictions:

```{r}
print(pred)
```

Lets compare these with the actuals:

```{r}
print(testdf$WillWait)
```

Make the agreement vector and calculate the accuracy which is the mean of the agreement vector:

```{r}
agreement <- (pred == testdf$WillWait)
agreement
mean(agreement)
```

