---
title: "R Exercises"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r, include=FALSE}
blanks<-TRUE
solution<-TRUE
```

Define a variable `x` and give it the value 24:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
x<-24
x
```

Define a variable `y` that is equal to `x + 5`

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
y<-x+5
y
```

Define a vector `w` that has three strings in it: “fee”, “fi”, “fum” 

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
w<-c("fee","fi","fum")
w
```

Change the 2nd entry of `w` to “foo” instead of “fi”. 

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
w[2] = "foo"
w
```

Define a new vector `k` by subsetting `w` with the selection vector `c(1,3)`. 

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
k<-w[c(1,3)]
k
```

Print out the length of `k` now after the subsetting

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
length(k)
```

Define a vector `v` that has elements: 10, 8, 3, 13, 24, 9, 3, 6, 7, 3

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
v<-c(10, 8, 3, 13, 24, 9, 3, 6, 7, 3)
v
```

Use subsetting to define a new vector `z` that only has entries that are bigger than 9:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
z<-v[v>9]
z
```

Define two vectors called `id` and `age`. 

In the `id` vector put 1001,1002,1003,1004,1005   

In the `age` vector put  18,16,26,15,22    

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
id<-c(1001,1002,1003,1004,1005)
age<-c(18,16,26,15,22)
id
age
```

Use subsetting to find the ids that have ages that are bigger than 17

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
newIds<-id[age>17]
newIds
```

For the following data: 

| custId | gender | spend |
|--------|--------|-------|
| 3203   | M      | 1200  |
| 3209   | F      | 963   |
| 3289   | M      | 356   |
| 3256   | F      | 567   |


Define a data frame with these columns:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
custId = c(3203, 3209, 3289, 3256)
gender = c("M", "F", "M", "F")
spend<-c(1200, 963, 356, 567)
df<-data.frame(custId, gender, spend)
df
```
For Customer 3289, use index(es) to change the spend amount to 415.

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
df[3,3] = 415
df
```

Print out just the `spend` column using the $ sign:

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
df$spend
```

Remove the Spend column and replace it with a new column called `discount`:

| discount |
|----------|
| 200      |
| 100      |
| 145      |
| 200      |

```{r, eval=FALSE, include=blanks}
PUT CODE HERE
```
```{r, include=solution}
df$spend <- NULL
df$discount <- c(200,100,145,200)
df
```
