---
title: "Rvest HM"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r echo=T, results='hide', message=F, warning=F}
if (!require("rvest")) install.packages("rvest")
library("rvest")
```

```{r, include=F}
ex<-T
```

We are going to read in a page at [https://www2.hm.com/en_us/sale/women/view-all.html](https://www2.hm.com/en_us/sale/women/view-all.html) and get the prices and sale prices on it:

```{r}
url<-"https://www2.hm.com/en_us/sale/women/view-all.html"
webpage <- read_html(url)
```

Use the selectorgadget to select the prices on the page.

- Enter the string expression for selecting the sale price 
```{r include=ex, eval=F}
nodes <- html_nodes(webpage, CODE)
price <- html_text(nodes)
str(price)
```
```{r include=!ex, eval=!ex}
nodes <- html_nodes(webpage, ".sale")
price <- html_text(nodes)
str(price)
```

Lets take a look at the first few values:

```{r, eval=!ex}
head(price)
```

- Enter the string expression for selecting the original price 
```{r include=ex, eval=F}
nodes <- html_nodes(webpage, CODE)
orig <- html_text(nodes)
str(orig)
```
```{r include=!ex, eval=!ex}
nodes <- html_nodes(webpage, ".regular")
orig <- html_text(nodes)
str(orig)
```

Lets take a look at the first few values:

```{r, eval=!ex}
head(orig)
```

- Enter the string expression for selecting the item name (make sure have 36 of these)
```{r include=ex, eval=F}
nodes <- html_nodes(webpage, CODE)
item <- html_text(nodes)
item<-trimws(item)
str(item)
```
```{r include=!ex, eval=!ex}
nodes <- html_nodes(webpage, ".item-heading")
item <- html_text(nodes)
item<-trimws(item)
str(item)
```

Lets take a look at the first few values:

```{r, eval=!ex}
df<-data.frame(item,price,orig)
df
```
