---
title: "Sales Based on Newspaper and Radio Ads"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

Just run this code block to set things up

```{r}
options(repr.plot.width=4, repr.plot.height=4)
options("scipen"=100, "digits"=4)
if (!require("RCurl")) install.packages("RCurl")
library("RCurl")
url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vT_oNaK_QKTtFQYdh7Pl17_prektSRuDVwRD71Vo8daBd0biyeG-Oiic4dMN_EL--voDWHAc5MmXNYH/pub?gid=0&single=true&output=csv"
textString<-getURL(url)
df<-read.csv(text=textString)
```

As a result of the above, the dataframe df has the Sales, Radio and Newspaper Ads data loaded in

#Sales Based on Radio and Newspaper Ads

```{r}
str(df)
```

Lets look at the correlation coefficient R for correlation between Newspaper and Sales

```{r}
R = cor(df$Newspaper, df$Sales)
R
R*R
```

If we did regression between Newspaper and Sales we would get this Rsquared

```{r}
plot(df$Newspaper,df$Sales)
```

You can fix up the x-axis label by using `xlab` and the y-axis label by using `ylab`. Also you can give the graph a title.

You can give the whole graph a title using `main`

You can also put in that they are filled dots instead of hollow by using `pch=19`

```{r}
plot(df$Newspaper,df$Sales, main="Newspaper Expenditures and Sales", xlab="Newspaper Ad Spending ($000)", ylab="Sales in Dollars ($000)", pch=19)
```

Here is the R squared for Radio and Sales

```{r}
R = cor(df$Radio, df$Sales)
R
R*R
```

```{r}
plot(df$Radio,df$Sales, main="Radio Ad Expenditures and Sales", xlab="Radio Ad Spending ($000)", ylab="Sales in Dollars ($000)", pch=19)
```

The following shows the correlation matrix

```{r}
cor(df)
```

```{r}
plot(df)
```

```{r}
plot(df, upper.panel = NULL, pch = 19, cex.labels=1.25)
```

```{r}
model = lm(Sales ~ Radio + Newspaper, data=df)
summary(model)
```

The regression equation is this:

$$ sales = 13.08(radio) + 16.80(newspaper) + 156.43 $$   
    
The standard error is:

$$ \text{standard error} = 159 $$ 

Test for overall significant of linear relationship:

$$ \text{p-value} = 0.00000015 $$

p-value for Radio:

$$ \text{p-value} = 0.00000049 $$

p-value for Newspaper:

$$ \text{p-value} = 0.00001831 $$


Make some predictions for:

1.   spending 30,000 on Radio ads and 35,000 on Newspaper 
2.   spending 35,000 on Radio ads and 45,000 on Newspaper 


```{r}
predictors = data.frame(Radio=c(30,40), Newspaper=c(35,45))
predictions<-predict(model, predictors)
round(predictions)
```

