---
title: "Predicting Sales from Newspaper and Radio Ads"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

Just run this code block to set things up:

```{r}
options("scipen"=100, "digits"=4)
url<- "https://docs.google.com/spreadsheets/d/e/2PACX-1vT_oNaK_QKTtFQYdh7Pl17_prektSRuDVwRD71Vo8daBd0biyeG-Oiic4dMN_EL--voDWHAc5MmXNYH/pub?gid=0&single=true&output=csv"
df<-read.csv(url)
```

```{r include=F}
ex<-F
```

As a result of the above, the dataframe has the sales and radio and newspaper ads data loaded in:

- print out some info on `df` using `str(df)`
- print out the first few lines of `df` using `head(df)`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
str(df)
head(df)
```

Lets look at the correlation coefficient R for Newspaper and Sales

- assign the correlation coefficient like this `R<-cor(df$newspaper, df$sales)`
- print out `R`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
R <- cor(df$newspaper,df$sales)
R
```

What about the scatterplot between them:

- Create a scatterpot with `plot` and pass it `df$newspaper` and `df$sales` as the x and y 
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
plot(df$newspaper, df$sales)
```

You can fix up the x-axis label by using `xlab` and the y-axis label by using `ylab`. Also you can give the graph a title using `main`.

You can also put in that they are filled dots instead of hollow by using `pch=19`

- run `plot` again, but add titles using arguments `main`, `xlab` and `ylab`. Also change the dots to be filled with `pch=19` 
- give it the `main` as: "Newspaper Expenditures and Sales"
- give it the `xlab` as: "Newspaper Ad Spending ($000)"
- give it the `ylab` as: "Sales in Dollars ($000)"
```{r include=ex, eval=F}
plot(df$newspaper,
     df$sales, 
     main=CODE, 
     xlab=CODE, 
     ylab=CODE", 
     pch=19)
```
```{r include=!ex}
#Original:
#plot(df$newspaper,
#     df$sales, 
#     main=CODE, 
#     xlab=CODE, 
#     ylab=CODE", 
#     pch=19)

plot(df$newspaper,
     df$sales, 
     main="Newspaper Expenditures and Sales", 
     xlab="Newspaper Ad Spending ($000)", 
     ylab="Sales in Dollars ($000)", 
     pch=19)
```

Here is the correlation coefficient R for Radio and Sales

- assign the correlation coefficient like this `R<-cor(df$radio, df$sales)`
- print out `R`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
R <- cor(df$radio, df$sales)
R
```

And here is the scatterplot for them:

- Create a scatterpot with `plot` and pass it `df$radio` and `df$sales` as the x and y 
- give it the `main` as: "Radio Ad Expenditures and Sales"
- give it the `xlab` as: "Radio Ad Spending ($000)"
- give it the `ylab` as: "Sales in Dollars ($000)"
```{r include=ex, eval=F}
plot(df$radio,df$sales, 
     main=CODE, 
     xlab=CODE, 
     ylab=CODE, 
     pch=19)
```
```{r include=!ex}
#Original:
#plot(df$radio,df$sales, 
#     main=CODE, 
#     xlab=CODE, 
#     ylab=CODE, 
#     pch=19)

plot(df$radio,df$sales, 
     main="Radio Ad Expenditures and Sales", 
     xlab="Radio Ad Spending ($000)", 
     ylab="Sales in Dollars ($000)", 
     pch=19)
```

The following shows the correlation matrix and the scatterplots for all variables:

- run `cor(df)` to show the correlation matrix
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
cor(df)
```

What are the correlations (Fill in the ???):

- between `newspaper` and `sales` ??? 
- between `radio` and `sales` ??? 
- between `newspaper` and `radio` ??? 

Now lets show the scatterplots:
- run `plot(df)`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
plot(df)
```

Lets fix up the plots a little just to look at the lower ones:

- run `plot` again but pass it `upper.panel=NULL` and `pch=19`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
plot(df, upper.panel = NULL, pch = 19) 
```

Lets run our regression model:

- assign `model` the result of `lm`, using `sales~radio+newspaper` as the first argument to `lm` and then `data=df` as the second argument
- call `summary(model)` to print out the regression model info after creating the model
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
model <- lm(sales ~ radio + newspaper, data=df)
summary(model)
```

FILL IN THE ???? below with the right values from above:

**Test for overall significant of linear relationship:**

overall p-value = ????

**Radio:**

p-value for radio = ???

**Newspaper:**

p-value for newspaper = ???

**The regression equation is this:**

sales = ???(radio) + ???(newspaper) + ???  
    
**The standard error is:**

standard error = ???     

#### Predictions

Make a dataframe to hold our predictors: 

- spending 30,000 on Radio ads and 35,000 on Newspaper 
- spending 35,000 on Radio ads and 45,000 on Newspaper 
- spending 5,000 on Radio ads and 60,000 on Newspaper 

Do this:  

- assign a vector `radio` to hold the two radio predictor values
- assign a vector `newspaper` to hold the two newspaper predictor values
- create a dataframe with `predictors<-data.frame(radio,newspaper)` 
- print `predictors` 
```{r include=ex, eval=F}
radio<-CODE
newspaper<-CODE
predictors <- data.frame(radio, newspaper)
predictors
```
```{r include=!ex}
# Original:
#radio<-CODE
#newspaper<-CODE
#predictors <- data.frame(radio, newspaper)
#predictors

radio<-c(30,40,5)
newspaper<-c(35,45,60)
predictors <- data.frame(radio, newspaper)
predictors
```

- make predictions with `predictions<-predict(model,predictors)` 
- print out the `predictions`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
predictions<-predict(model, predictors)
predictions
```

Fill in the correct answers below:

- Prediction for \$30,000 on Radio and \$35,000 on Newspaper: ??? 
- Prediction for \$35,000 on Radio and \$45,000 on Newspaper: ??? 
- Prediction for \$5,000 on Radio and \$60,000 on Newspaper: ??? 

