---
title: "Customer Satisfaction and Loyalty"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r echo=T, results='hide', message=F, warning=F}
options("scipen"=100, "digits"=4)
if(!require("readr")) install.packages("readr")
library("readr")
```
This example comes from here: [Using Cluster Analysis for Market Segmentation](https://www.segmentationstudyguide.com/using-cluster-analysis-for-market-segmentation/)

In this case there is no prediction made for the data. This is an example of "unsupervised" machine learning.

Lets read in the data:

```{r}
url<-"cust-satisf-loyalty.csv"
url<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vRfKqtNd28lmHr259w6Uoeisf7uY9UtxhUeiNnQlULHbD-MPLHN4cQE26adB2R63g0IrWDuadx2doRN/pub?gid=0&single=true&output=csv"
df<-read.csv(url, stringsAsFactors=TRUE)
str(df)
```
Lets see a plot of the data as well:

```{r}
plot(df, pch=19, main="Customer Satisfaction and Loyalty", xlab="Customer Satisfaction", ylab="Loyalty", xlim=c(0,100), ylim=c(0,100))
```

Here is the setup from that website:

>Let’s assume that we have customer satisfaction (CSAT) scores of 1 to 99 (where 1 = very dissatisfied and 90 = very satisfied). And we have similar scores for the customer’s level of loyalty (1 = high switcher-low loyalty and 99 = non-switcher-high loyalty).

Lets cluster into 2 clusters:   

```{r}
set.seed(1)
model<-kmeans(df,2,nstart=20)
print(model)
```

Let's see a plot of the 2 clusters:   

```{r}
plot(df, pch=19, main="Customer Satisfaction and Loyalty", xlab="Customer Satisfaction", ylab="Loyalty", col=model$cluster, xlim=c(0,100), ylim=c(0,100))
```

Now lets cluster into 3 clusters:   

```{r}
set.seed(1)
model<-kmeans(df,3,nstart=20)
plot(df, pch=19, main="Customer Satisfaction and Loyalty", xlab="Customer Satisfaction", ylab="Loyalty", col=model$cluster, xlim=c(0,100), ylim=c(0,100))
```

Lets cluster into 4 clusters:   

```{r}
set.seed(1)
model<-kmeans(df,4,nstart=20)
plot(df, pch=19, main="Customer Satisfaction and Loyalty", xlab="Customer Satisfaction", ylab="Loyalty", col=model$cluster, xlim=c(0,100), ylim=c(0,100))
```

Lets cluster into 5 clusters:   

```{r}
set.seed(1)
model<-kmeans(df,5,nstart=20)
plot(df, pch=19, main="Customer Satisfaction and Loyalty", xlab="Customer Satisfaction", ylab="Loyalty", col=model$cluster, xlim=c(0,100), ylim=c(0,100))
```

What might be an interpretation of these different clusters. 


