---
title: "Sequences"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

We are going to take a look at a simple way to create vectors of numbers.   

For example suppose we want a vector with just "1,2,3,4,5,6" on it.

```{r}
a <- 1:6
a
```

The notation `1:6` means the same here as `c(1,2,3,4,5,6)`. That is we create a vector using the combine function `c` with the 6 numbers we want. This is called a "sequence" in R, since the numbers are listed in order.  

Sequences are a great way to get certain vectors where the numbers have some pattern to them.

What happens if we want to make the numbers "count down" from something:


```{r}
b <- 6:1
b
```

Can we start at something other than 1:

```{r}
c <- 4:9
c
```

Can we start at a negative number 

```{r}
d <- -3:4
d
```

If we use the `seq` function we an create sequences and "count by" whatever value we want. Below we start at 3 and count by 2s up to 21. 

```{r}
e <- seq(from=3, to=21, by=2) 
e
```

Now lets count by 5, starting at 0 and go up to 50:

```{r}
f <- seq(from=0, to=50, by=5) 
f
```
