---
params:
  a:
    input: slider
    label: This is a
    max: 50
    min: 1
    step: 3
    value: 40
  b:
    input: slider
    label: This is b
    max: 80
    min: 50
    step: 1
    value: 60
  c:
    input: numeric
    label: This is c
    max: 80
    min: 50
    step: 5
    value: 75
  gender:
    choices:
    - male
    - female
    inline: yes
    input: radio
    label: 'Gender:'
    value: male
  region:
    choices:
    - east
    - west
    - north
    - south
    input: select
    label: 'Region:'
    value: north
  word:
    input: text
    label: 'Word of the day:'
    placeholder: Type the word of the day
    value: 'nothing'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
dnorm_limit <- function(x) {
 y <- dnorm(x)
 y[x < -1.2 | x > 1.53] <- NA
 return(y)
}
```

# Simple with markdown and code 

You can also embed plots, for example here are some:

```{r area, echo=FALSE}
#change dev to svg if need to
dat <- data.frame(x=c(-3.5, 3.5))
ggplot(dat, aes(x=x)) +
stat_function(fun=dnorm_limit, geom="area", fill="blue", alpha=0.5) +
stat_function(fun=dnorm) +
labs(x = "z", y = "") +
geom_hline(yintercept=0) +
scale_x_continuous(breaks = seq(-3, 3, by = 1.0)) +
scale_y_continuous(breaks = seq(0, .4, by = 0.2)) +
annotate("text", x = 1.5, y = -0.01, label = "z=1.53") +
annotate("text", x = -1.2, y = -0.01, label = "z=-1.2")
```

My Parameters
- a is `r params$a` and the fraction is \(\frac{`r params$a`}{4}\)
- b is `r params$b` $\frac{3}{2343434}$
blah what 

# Parameter a is `r params$a` and b is `r params$b` 
1. The region is `r params$region`
2. The gender is `r params$gender`
    * Unordered sub-list. 
3. The value of c is `r params$c` 
    1. Ordered sublist
    2. number 2 on the ordered sublist
4. The word of the day is: `r params$word`.

   Inline style double backslash paren style \(\frac{3}{4}\) blah

   Inline code style  backslash paren style \(\frac{`r params$a`}{4}\)

```{r equation, echo=FALSE}
x<-params$a; 
mu<-params$b; 
numer<-(x-mu); 
sigma<-1.2; 
z<-(x-mu)/sigma
```

Here ne with inline r code chunks:

$$ z=\frac{x-\mu}{\sigma}=\frac{`r x`-`r mu`}{`r sigma`}=\frac{`r numer`}{`r sigma`}=`r z` $$

And that is all!!!!!!!!
