---
title: "Standard Normal Curve Area Between"
params:
  a:
    input: numeric
    label: a 
    max: 3.5
    min: -3.5
    step: .1
    value: 2.0 
  b:
    input: numeric
    label: b
    max: 3.5
    min: -3.5
    step: .1
    value: -3.5 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# a<-params$a
# b<-params$b
a<- -1.0
b<- 2.1
library(ggplot2)
```

## Area under normal curve between two values

Hi

We are going to find the area between the two z-values by using the standard normal (z) table:

Here $a =`r a`$ and $b =`r b`$

Here is a picture of the area that we want:

```{r area, echo=FALSE}
#change dev to svg if need to

dat <- data.frame(x=c(-3.5, 3.5))
labelA <- sprintf("a = %s",a)
labelB <- sprintf("b = %s",b)
ggplot(dat, aes(x=x)) +
	stat_function(fun=dnorm) +   
	stat_function(fun=dnorm,     
		      xlim = c(a,b), 
		      geom="area", 
		      fill="green", 
		      alpha=0.3) +
	labs(x = "Z", y = "") +       
	geom_hline(yintercept=0) +
	scale_x_continuous(breaks = seq(-3, 3, by = 1.0)) +
	scale_y_continuous(breaks = seq(0, .4, by = 0.2)) +
	annotate("text", 
		 x = a, 
		 y = -0.01, 
		 label = labelA) +
	annotate("text", 
		 x = b, 
		 y = -0.01, 
		 label = labelB)
```

First we find the left tail area for z-value on the right: $b =`r b`$

```{r areab, echo = FALSE}
areaB <- round(pnorm(b),4)
```
$$
\text{left tail area for b} = `r areaB`
$$

Then we find the left tail area for the z-value on the left $a =`r a`$:

```{r areaA, echo = FALSE}
areaA <- round(pnorm(a),4)
```
$$
\text{left tail area for a} = `r areaA`
$$

Finally we find the area between the two z-values by subtracting the left tail area up to b by the left tail area up to a. This leaves us with the area between the two z-values:

$$
\text{area between}=`r areaB` - `r areaA`=`r round(areaB-areaA, 4)`
$$
