---
title: "TShirt Size Using (Classification) Decision Tree"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r, include=FALSE}
ex<-T
```

```{r echo=T, results='hide', message=F, warning=F}
options("scipen"=100, "digits"=4)

if(!require("rpart")) install.packages("rpart")
if(!require("rpart.plot")) install.packages("rpart.plot")
if(!require("Metrics")) install.packages("Metrics")

library("rpart")
library("rpart.plot")
library("Metrics")
```

## Predicting TShirt Size using Decision Tree 


## Training Data

First lets take a look at the data we will work with. 

So here is the data we have, this will be our training data:

- `Size` is our result or outcome
- `Height` and `Weight` are the predictors

```{r}
trainurl<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vQb1-HxaC0FoyX5qGgAqcYRIVS5eZqwwfnECQucfqZ-Kn-65Pdacy80UX4K2AAJQH0WwgPd_OH_6Y7d/pub?gid=0&single=true&output=csv"
train<-read.csv(trainurl)
str(train)
```

 - Print out the info of the data frame using `str(train)`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex, eval=!ex}
str(train)
```

Now let's print out the training set to make sure we read it correctly:

- Print out the the data frame using `print(train)`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex, eval=!ex}
print(train)
```

## Testing Data 

Next let's look at some data that we can use as a testing set. This data we will use to evaluate how well the models we looked at above will do when they see "new" data. This gives a better idea of how accurate our model is.

First we read the test set and look at its structure:

```{r}
testurl<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vQb1-HxaC0FoyX5qGgAqcYRIVS5eZqwwfnECQucfqZ-Kn-65Pdacy80UX4K2AAJQH0WwgPd_OH_6Y7d/pub?gid=15577345&single=true&output=csv"
test<-read.csv(testurl)
```

 - Print out the info of this data frame using `str(test)`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex, eval=!ex}
str(test)
```

And now print out the test set:

- Print out the the data frame using `print(test)`
```{r include=ex, eval=F}
CODE
```
```{r include=!ex, eval=!ex}
print(test)
```

### Model 1 - use `Height` to predict `Size` 

#### Training

- Put in the right model for modeling `Size` based just on `Height` 
```{r include=ex, eval=FALSE}
control = rpart.control(minsplit=1,maxdepth=1)
model <- rpart(CODE, data=train, method="class", control = control)
rpart.plot(model, type=4, extra = 1, digits=-2)
```
```{r include=!ex, eval=!ex}
control = rpart.control(minsplit=1,maxdepth=1)
model <- rpart(Size~Height, data=train, method="class", control = control)
rpart.plot(model, type=4, extra = 1, digits=-2)
```

#### Testing

Now lets do a prediction:

- Make predictions and create a dataframe by running the code below:
```{r, eval=!ex}
pred <- predict(model, newdata = test, type = 'class')
compare <- data.frame(actual=test$Size, predictions=pred)
print(compare)
```

And lets find the confusion matrix 

- Create the confusion matrix by passing `test$Size` and `pred` to the `table` function:
```{r include=ex, eval=FALSE}
table(CODE)
```
```{r include=!ex, eval=!ex}
table(test$Size, pred)
```

Here is the accuracy:

- calculate the accuracy passing `test$Size` and `pred` to the `accuracy` function:
```{r include=ex, eval=FALSE}
accuracy(CODE)
```
```{r include=!ex, eval=!ex}
accuracy(test$Size, pred)
```

### Model 2 - use `Weight` to predict `Size` 

#### Training

- Put in the right model for modeling `Size` based just on `Weight` 
```{r include=ex, eval=FALSE}
control = rpart.control(minsplit=1,maxdepth=1)
model <- rpart(CODE, data=train, method="class", control = control)
rpart.plot(model, type=4, extra = 1, digits=-2)
```
```{r include=!ex, eval=!ex}
control = rpart.control(minsplit=1,maxdepth=1)
model <- rpart(Size~Weight, data=train, method="class", control = control)
rpart.plot(model, type=4, extra = 1, digits=-2)
```

#### Testing

Now lets do a prediction:

- Make predictions and create a dataframe by running the code below:
```{r, eval=!ex}
pred <- predict(model, newdata = test, type = 'class')
compare <- data.frame(actual=test$Size, predictions=pred)
print(compare)
```

And lets find the confusion matrix 

- Create the confusion matrix by passing `test$Size` and `pred` to the `table` function:
```{r include=ex, eval=FALSE}
table(CODE)
```
```{r include=!ex, eval=!ex}
table(test$Size, pred)
```

Here is the accuracy:

- calculate the accuracy passing `test$Size` and `pred` to the `accuracy` function:
```{r include=ex, eval=FALSE}
accuracy(CODE)
```
```{r include=!ex, eval=!ex}
accuracy(test$Size, pred)
```


### Model 3 - use `Height` and `Weight` to predict `Size` 

#### Training

- Put in the right model for modeling `Size` based just on `Weight` and `Height` 
```{r include=ex, eval=FALSE}
control = rpart.control(minsplit=1,maxdepth=2)
model <- rpart(CODE, data=train, method="class", control = control)
rpart.plot(model, type=4, extra = 1, digits=-2)
```
```{r include=!ex, eval=!ex}
control = rpart.control(minsplit=1,maxdepth=2)
model <- rpart(Size~Height+Weight, data=train, method="class", control = control)
rpart.plot(model, type=4, extra = 1, digits=-2)
```

#### Testing

Now lets do a prediction:

- Make predictions and create a dataframe by running the code below:
```{r, eval=!ex}
pred <- predict(model, newdata = test, type = 'class')
compare <- data.frame(actual=test$Size, predictions=pred)
print(compare)
```

And lets find the confusion matrix 

- Create the confusion matrix by passing `test$Size` and `pred` to the `table` function:
```{r include=ex, eval=FALSE}
table(CODE)
```
```{r include=!ex, eval=!ex}
table(test$Size, pred)
```

Here is the accuracy:

- calculate the accuracy passing `test$Size` and `pred` to the `accuracy` function:
```{r include=ex, eval=FALSE}
accuracy(CODE)
```
```{r include=!ex, eval=!ex}
accuracy(test$Size, pred)
```

