---
title: "Predicting TShirt Size"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r echo=T, results='hide', message=F, warning=F}
options(repr.plot.width=4, repr.plot.height=4)
options("scipen"=100, "digits"=4)
if(!require("readr")) install.packages("readr")
if(!require("knitr")) install.packages("knitr")
if(!require("Metrics")) install.packages("Metrics")
if(!require("class")) install.packages("class")
library("readr")
library("Metrics")
library("class")
library("knitr")
knitr::opts_chunk$set(fig.width=4, fig.height=4)
normalize <- function(x) {
    return ( (x-min(x))/(max(x)-min(x)) )
}
```

## Predicting TShirt Size using KNN 


First lets take a look at the data we will work with. 

So here is the data we have, this will be our training data:

- `Size` is our result or outcome
- `Height`, `Weight` are the predictors

We hope that we can predict the T Shirt size from the Height and Weight:   

| Height | Weight | Size |
|--------|--------|------|
| 158    | 59     | M    |
| 160    | 59     | M    |
| 160    | 60     | M    |
| 163    | 61     | M    |
| 160    | 64     | L    |
| 165    | 61     | L    |
| 165    | 62     | L    |
| 168    | 62     | L    |
| 168    | 63     | L    |
| 170    | 63     | L    |
| 170    | 68     | L    |

```{r}
trainurl<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vQb1-HxaC0FoyX5qGgAqcYRIVS5eZqwwfnECQucfqZ-Kn-65Pdacy80UX4K2AAJQH0WwgPd_OH_6Y7d/pub?gid=0&single=true&output=csv"
traindf<-read.csv(trainurl, stringsAsFactors=TRUE)
str(traindf)
```
Now let's print out the training set to make sure we read it correctly:

```{r}
print(traindf)
```

Lets take a look at the data as well:

```{r}
plot(traindf$Height, traindf$Weight, col=traindf$Size, pch=19, xlim=c(155,175), ylim=c(55,70))
```

We also need a testing data set so here it is:

| Height | Weight | Size |
|--------|--------|------|
| 158    | 58     | M    |
| 158    | 63     | M    |
| 163    | 60     | M    |
| 163    | 64     | L    |
| 165    | 65     | L    |
| 168    | 66     | L    |
| 170    | 64     | L    |

```{r}
testurl<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vQb1-HxaC0FoyX5qGgAqcYRIVS5eZqwwfnECQucfqZ-Kn-65Pdacy80UX4K2AAJQH0WwgPd_OH_6Y7d/pub?gid=15577345&single=true&output=csv"
testdf<-read.csv(testurl, stringsAsFactors=TRUE)
str(testdf)
```

```{r}
print(testdf)
```

Now lets extract the last column of the train dataset since we need it as the 'cl' argument in the knn function. We also remove the `Shirt` column from the data frames since knn expects the dataframes to have no result columns 

```{r}
train_target <- traindf$Size
traindf$Size <- NULL

test_target <- testdf$Size 
testdf$Size <- NULL

traindf_n <- as.data.frame(lapply(traindf, normalize))
testdf_n <- as.data.frame(lapply(testdf, normalize))

set.seed(1234)
prediction<-knn(traindf_n,testdf_n, cl=train_target, k=3)
print(prediction)
```

We put the actuals and predictions back into the test data frame so we can check accuracy:

```{r}
testdf$Size <- test_target
testdf$Prediction <- prediction
print(testdf)
```

Here is the confusion matrix and the accuracy:

```{r}
table(prediction=prediction,actual=test_target)
accuracy(test_target, prediction)
```

First we normalize the predictors for those test values:

```{r}
normHeight<-normalize(testdf_n$Height)
normWeight<-normalize(testdf_n$Weight)
```
Now lets examine the 1st data value in the test set:

```{r}
plot(traindf_n$Height, traindf_n$Weight, col=train_target, pch=19, xlab="Height", ylab="Weight", xaxt='n', yaxt='n') 
points(normHeight[1], normWeight[1], pch=19, col="blue")
print(testdf[1,])
```
Here is the 2nd data value in the testing set:

```{r}
plot(traindf_n$Height, traindf_n$Weight, col=train_target, pch=19, xlab="Height", ylab="Weight", xaxt='n', yaxt='n') 
points(normHeight[2], normWeight[2], pch=19, col="blue")
print(testdf[2,])
```

Here is the 3rd data value in the testing set:

```{r}
plot(traindf_n$Height, traindf_n$Weight, col=train_target, pch=19, xlab="Height", ylab="Weight", xaxt='n', yaxt='n') 
points(normHeight[3], normWeight[3], pch=19, col="blue")
print(testdf[3,])
```

Here is the 4rd data value in the testing set:

```{r}
plot(traindf_n$Height, traindf_n$Weight, col=train_target, pch=19, xlab="Height", ylab="Weight", xaxt='n', yaxt='n') 
points(normHeight[4], normWeight[4], pch=19, col="blue")
print(testdf[4,])
```

Here is the 5rd data value in the testing set:

```{r}
plot(traindf_n$Height, traindf_n$Weight, col=train_target, pch=19, xlab="Height", ylab="Weight", xaxt='n', yaxt='n') 
points(normHeight[5], normWeight[5], pch=19, col="blue")
print(testdf[5,])
```
