---
title: "Two Products"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r echo=T, results='hide', message=F, warning=F}
options("scipen"=100, "digits"=4)

if(!require("rpart")) install.packages("rpart")
if(!require("rpart.plot")) install.packages("rpart.plot")
if(!require("Metrics")) install.packages("Metrics")

library("rpart")
library("rpart.plot")
library("Metrics")
```

## Load the Training Data 

```{r}
url<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vTFmRX4RW3PitgcJya0X2sRbSiD0J2t0oYewyhkkyWwR9i8NIaHiuQKrBtLlrwG9fzn4MvNOM92olnK/pub?gid=0&single=true&output=csv"
train<-read.csv(url)
str(train)
```

Here is the original data frame. There are two predictors `gender` and `age` and the result we are trying predict is `product`, which is the product they will buy. 

```{r}
print(train)
```

## Load the Testing Data 

```{r}
url<-"https://docs.google.com/spreadsheets/d/e/2PACX-1vTFmRX4RW3PitgcJya0X2sRbSiD0J2t0oYewyhkkyWwR9i8NIaHiuQKrBtLlrwG9fzn4MvNOM92olnK/pub?gid=1744064271&single=true&output=csv"
test<-read.csv(url)
str(test)
```

```{r}
print(test)
```

### Model 1 - Split on Gender 

#### Train with Training Data

Lets sort it by gender:

```{r}
print(train[order(train$gender),])
```

So if we split on gender here is what we would get:

```{r}
model <- rpart(product~gender, 
               data=train, 
               control = rpart.control(minsplit=1, maxdepth=1),
               method="class")
rpart.plot(model, type=4, extra = 1, digits=-2)
```

The tree above makes 1 mistake out of 7.

#### Test With Testing Data

Here are the predictions for our test data:

```{r}
pred <- predict(model, newdata = test, type = 'class')
compare <- data.frame(actual=test, predictions=pred)
print(compare)
```

Here is the confusion matrix:

```{r}
table(test$product, pred)
```

Here is the accuracy:

```{r}
accuracy(test$product, pred)
```

### Model 2 - Split on Age 

#### Train with Training Data

Lets sort it by age:

```{r}
print(train[order(train$age),])
```

```{r}
model <- rpart(product~age, 
               data=train, 
               control = rpart.control(minsplit=1, maxdepth=1, cp=-1),
               method="class")
rpart.plot(model, type=4, extra = 1, digits=-2)
```

The tree above makes 2 mistake out of 7.

#### Test With Testing Data

Here are the predictions for our test data:

```{r}
pred <- predict(model, newdata = test, type = 'class')
compare <- data.frame(actual=test, predictions=pred)
print(compare)
```

Here is the confusion matrix:

```{r}
table(test$product, pred)
```

Here is the accuracy:

```{r}
accuracy(test$product, pred)
```

### Model 3 - Split on Gender, then Age 

#### Train with Training Data

```{r}
model <- rpart(product~gender+age, 
               data=train, 
               control = rpart.control(minsplit=1, maxdepth=3),
               method="class")
rpart.plot(model, type=4, extra = 1, digits=-2)
```

#### Test With Testing Data

Here are the predictions for our test data:

```{r}
pred <- predict(model, newdata = test, type = 'class')
compare <- data.frame(actual=test, predictions=pred)
print(compare)
```

Here is the confusion matrix:

```{r}
table(test$product, pred)
```

Here is the accuracy:

```{r}
accuracy(test$product, pred)
```
The best model on these training sets is the last one, since the accuracy is smallest for that one.
