---
title: "More Variables"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

```{r include=F}
ex<-T
```

In the code block below (replace the word `CODE`):

- Store the number 8 in a variable called `x` 
- Print out `x`
- Execute the code block   


```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
x<-8
x
```

The output of the above should be `8` 

In the code block below:

- Now assign `y` to be `5*x+3`
- Print out `y` 
- Execute the code block   

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
y<-5*x+3
y
```

The output of the above should be `43` 

In the code block below:

- Find the square root of 119025 using the function `sqrt` 
- Execute the code block   

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
sqrt(119025)
```
The output of the above should be `345` 


In the code block below:

- Use the function `ceiling` to round up the value `1.3` 
- Execute the code block   

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
ceiling(1.3)
```

The output of the above should be `2` 

In the code block below:

- Use the function `floor` to round down the value `3.8` 
- Execute the code block   

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
floor(3.8)
```

The output of the above should be `3` 

In the code block below:

- Store a new number 10 in the variable called `x`. 
- Print out `x`
- Execute the code block   

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
x<-10
x
```

The output of the above should be `10` 

In the code block below:

- Assign the variable `myVal` to be `x+y`
- Print out `myVal`
- Execute the code block   

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
myVal <-x+y
myVal
```
The output of the above should be `53` 

In the code block below:

- Enter and the expression `14/2-1+3` 
- Execute the code block, it outputs  `9` 
- Put in parentheses so that it outputs `17` instead 

```{r include=ex, eval=F}
14/2-1+3
```
```{r include=!ex}
14/2-1+3
```

In the code block below:

- Enter and the expression `8*3+9-9` 
- Execute the code block, it outputs  `24` 
- Put in parentheses so that it outputs `87` instead 

```{r include=ex, eval=F}
8*3+9-9
```
```{r include=!ex}
8*(3+9)-9
```

In the code block below:

- Enter and the expression `8*3+9-9` 
- Execute the code block, it outputs  `24` 
- Put in parentheses so that it outputs `87` instead 

```{r include=ex, eval=F}
8*3+9-9
```
```{r include=!ex}
8*(3+9)-9
```

In the code block below:

- Enter and the expression `10-9*24/8*6` 
- Execute the code block, it outputs  `-152` 
- Put in parentheses so that it outputs `18` instead 

```{r include=ex, eval=F}
10-9*24/8*6
```
```{r include=!ex}
(10-9)*24/8*6
```

In the code block below:

- Assume you have this code `5(3)`
- Execute the code block, it outputs  an error 
- Fix the code so that it outputs 15 

```{r include=ex, eval=F}
5(3)
```
```{r include=!ex}
5*3
```

- Assign a variable `z<-7` 
- Try to print out this expression: `2z` 
- Execute the code, it outputs  an error 
- Fix the code so that it outputs `14` 

```{r include=ex, eval=F}
z<-7
2z
```
```{r include=!ex}
z<-7
2*z
```
