---
title: "Vectors"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

Vectors are lists of elements of the same type. They are an extremely important data structure in R.  

Vectors are created using the `c` function, which stands for "combine".
 
```{r}
x<-c(3,7.4,-3, 3.2)
x
```

This vector has class 'numeric' and has 4 elements. We can see by using the `length` function:

```{r}
class(x)
length(x)
```

Lets take a look at the 'structure' of x using the `str` function:

```{r}
str(x)
```

```{r include=FALSE, eval=FALSE}
knitr::knit_exit()
```

The following vector has class 'character' and its length is 3:

```{r}
y<-c("Goodbye", "Hello", "Goodnight")
y
class(y)
length(y)
```

The following vector has class 'logical' and its length is 5:

```{r}
z<-c(TRUE, FALSE, TRUE, FALSE, FALSE)
z
class(z)
length(z)
```
Notice each vector has to have the same type for each of its elements.  

1.  `x` is a vector of class 'numeric'
1.  `y` is a vector of class 'character'
1.  `z` is a vector of class 'logical'

What would happen if we try to combine components that had different classes?
```{r, error=TRUE}
a<-c(TRUE, 4.5, "hello")
a
```

```{r}
str(a)
```

At first it looks like this worked, but notice how each element is a 'character' now:

```{r}
class(a)
```

What happened? Here we tried to create a vector whose elements were different types.  

When we did that R went ahead and did it, but it made each element a string. 

Some of the big advantages of vectors has to do with math we can do with them. It turns out that vectors can simplify a lot of the calculations you might want to do in data science.   

Lets try to add two vectors:

```{r}
x<-c(2,4,3,1)
y<-c(3,6,1,9)
x+y
```

What about multiplying them together:

```{r}
w<-c(2,4,3,1)
z<-c(3,6,1,9)
w*z
```

Or multiplying a vector by a number:

```{r}
a<-c(2,4,3,1)
5*a
```

Suppose we want to access the elements in a vector. You can access the elements in a vector by using the "subscript" notation. This means you refer to the different elements using an index:

```{r}
b<-c(4,3,-1,2)
b[1]
b[2]
b[3]
b[4]
```

The first index is 1 and the last index is 4 for this vector. In some programming languages the first element in a vector would be refered to with an index of 0, not 1.

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

