---
title: "Vectors In Class"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

```{r include=F}
ex<-F
```

## Using Vectors for Multiple Regression

Let's use vectors to describe a multiple regression. 

Suppose we have run a regression analysis and we have three x-variables $x_1, x_2, x_3$ and we want to predict $y$ from those predictors. Let's assume we have three slopes and an intercept given by:

$$ 
m = (m_1, m_2, m_3) = (5,-1,2) 
$$

$$ 
b = 7
$$

These may have come from `LINEST` in a spreadsheet or they may have come from using R's `lm` function.

- Create a vector `m` with the values 5,-1,2
- print `m`

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
m<-c(5,-1,2)
m
```

- Use the function `str` to print out info about the vector `m` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
str(m)
```

## Making Predictions with a Vector of Predictors

Now suppose we want to do some predictions using our regression equation.

- Create a vector `x` with the values 1,4,3 
- print `x`

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
x<-c(1,4,3)
x
```

- Assign `7` to a variable `b` 
- Assign `sum(m*x)+b` to a variable `y` 
- Print out `y` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
b<-7
y<-sum(m*x)+b
y
```

That output is our prediction of $y$ when $x = (1,4,3)$, which means when $x_1=1$, $x_2=4$ and $x_3=3$. 

This is exactly like computing a prediction using a regression equation as follows:

$$ y = m_1(x_1) + m_2(x_2) + m_3(x_3) + b $$ 

where `m` is a vector with the slopes:

$$ m = (m_1, m_2, m_3) = (5,-1,2) $$

and `x` is a vector with the x-values: 

$$ x = (x_1, x_2, x_3) = (1,4,3) $$

So that this is calculation is like a prediction using the x-values:

$$ y = m_1(x_1) + m_2(x_2) + m_3(x_3) + b = 5(1) + -1(4) + 2(3) + 7 = 14 $$ 

Lets make an additional prediction when `x<-c(2,5,4)` 

- Assign `x` to a be a vector with three elements, 2,5,4  
- Assign `sum(m*x)+b` to a variable `y` 
- Print out `y` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
x<-c(2,5,4)
y<-sum(m*x)+b
y
```

## Scatterplots using Vectors 

Lets also see how vectors can be used to show some plots in R. First we show a scatterplot made by vectors of `x` and `y`. 

- Assign `x` to a be a vector with three elements, 2,5,4,6,7,8  
- Assign `y` to a be a vector with three elements, 3,5,6,6,8,8  
- Print out `x` 
- Print out `y` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
x<-c(2,5,4,6,7,8)
y<-c(3,5,6,6,8,8)
```

- call the function `plot` and pass it the `x` and `y` you just created 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
plot(x,y)
```

This is your first graph in R! 

## Regression Modeling using Vectors 

Its also very easy to create a regression analysis in R if you have the `x` and `y` data as vectors. 

- Type the code `model<-lm(y~x)` on the first line below to set up a regression analysis
- Type the code `summary(model)` to get the regression output with info about the model  

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
model<-lm(y~x)
summary(model)
```
