---
title: "Vectors"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

Vectors are lists of elements of the same type. They are an extremely important data structure in R.  

Vectors are created using the `c` function, which stands for "combine".
 
```{r}
x<-c(3,7.4,-3, 3.2)
x
```

This vector has class 'numeric' and length 4:

```{r}
class(x)
length(x)
```

Lets take a look at the 'structure' of x using the `str` function:

```{r}
str(x)
```

```{r include=FALSE, eval=FALSE}
knitr::knit_exit()
```

The following vector has class 'character' and the length is 3:

```{r}
y<-c("Goodbye", "Hello", "Goodnight")
y
class(y)
length(y)
```

The following vector has class 'logical' and the length is 5:

```{r}
z<-c(TRUE, FALSE, TRUE, FALSE, FALSE)
z
class(z)
length(z)
```
Notice each vector has to have the same types for each of its components.  

1.  `x` is a vector of class 'numeric'
1.  `y` is a vector of class 'character'
1.  `z` is a vector of class 'logical'

What would happen if we try to combine components that had different classes?
```{r, error=TRUE}
a<-c(TRUE, 4.5, "hello")
a
```

```{r}
str(a)
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

