---
title: "DataTypes and Vectors HW"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

```{r include=F}
ex<-F
```

## Data Types Practice

- Assign a character (string) `u` with the value "5.16" (include the quotes)
- print `u`
- use `str` to print out info on `u`

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
u<-"5.16"
u
str(u)
```

- Use the `as.numeric` function to convert the above `u` and assign it to a numeric variable `v` 
- print `v`
- use `str` to print out info on `v`

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
v<-as.numeric(u)
v
str(v)
```

Discover the data types of the following expressions:

|Expression|
|-|
|-2|
|2.32|
|TRUE|
|"FALSE"|
|"hi"|
|"6L"|
|"bye bye"|
|c("bye","bye")|
|c(2,3)|
|c("2","3")|
|c("2.34", "hello")|

- Use `str` on each of the above to discover their data types 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
str(-2)
str(2.32)
str(TRUE)
str("FALSE")
str("hi")
str("6L")
str("bye bye")
str(c("bye","bye"))
str(c(2,3))
str(c("2","3"))
str(c("2.34", "hello"))
```

## Multiple Regression Equation with 15 predictors 

Here are the coefficients from the predictors in a multiple regression for predicting pregnancy (with a \"pregnancy score\") from the purchasing behavior of customers: 

|  | Coefficients |
|-|-|
| Pregnancy Test | 0.218058401 |
| Birth Control | -0.274472752 |
| Feminine Hygiene | -0.245079751 |
| Folic Acid | 0.34405342 |
| Prenatal Vitamins | 0.298086596 |
| Prenatal Yoga | 0.318919562 |
| Body Pillow | 0.184546094 |
| Ginger Ale | 0.226086097 |
| Sea Bands | 0.140434527 |
| Stopped buying cigarettes | 0.159818146 |
| Cigarettes | -0.164941603 |
| Smoking Cessation | 0.165721439 |
| Stopped buying wine | 0.191146551 |
| Wine | -0.207701535 |
| Maternity Clothes | 0.240508913 |

And here is the intercept

| Intercept |
|-|
| 0.413672294|

These may have come from `LINEST` in a spreadsheet or they may have come from using R's `lm` function.

- Create a vector `m` with the 15 values above
- print `m`

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
m<- c(0.218058401, -0.274472752, -0.245079751, 0.34405342, 0.298086596, 0.318919562, 0.184546094, 0.226086097, 0.140434527, 0.159818146, -0.164941603, 0.165721439, 0.191146551, -0.207701535, 0.240508913)
m
```

- Use the function `str` to print out info about the vector `m` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
str(m)
```

## Making Predictions with the Vector of Predictors

Now suppose we want to do some predictions using our regression equation.

Here is one prediction we want to do:

| PregnancyTest | BirthControl | FeminineHygiene | FolicAcid | PrenatalVitamins | PrenatalYoga | BodyPillow | GingerAle | SeaBands | StoppedBuyingCigerettes | Cigarettes | SmokingCessation | StoppedBuyingWine | Wine | MaternityClothes |
|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|
| 1 | 0 | 0 | 0 | 1 | 0 | 0 | 0 | 0 | 1 | 0 | 1 | 1 | 0 | 0 |


- Create a vector `x` with the values above  
- print `x`

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
x<-c(1,0,0,0,1,0,0,0,0,1,0,1,1,0,0)
x
```

- Assign the intecept value to a variable `b` 
- Assign `sum(m*x)+b` to a variable `y1` 
- Print out `y1` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
b<-0.413672294
y1<-sum(m*x)+b
y1
```

| PregnancyTest | BirthControl | FeminineHygiene | FolicAcid | PrenatalVitamins | PrenatalYoga | BodyPillow | GingerAle | SeaBands | StoppedBuyingCigerettes | Cigarettes | SmokingCessation | StoppedBuyingWine | Wine | MaternityClothes |
|-|-|-|-|-|-|-|-|-|-|-|-|-|-|-|
|0|1|0|0|0|0|0|0|0|0|1|0|0|1|0

- Create a vector `x` with the values above  
- Assign `sum(m*x)+b` to a variable `y2` 
- Print out `y2` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
x<-c(0,1,0,0,0,0,0,0,0,0,1,0,0,1,0)
y2<-sum(m*x)+b
y2
```

Does the value of these predictions lead you to conclude the customer is pregnant?  

|prediction 1 | prediction 2 
|-|-|
| 1.45 | -0.23 |

One of the predictions was positive and one was negative. What do you think this means here? Can you guess?

