---
title: "Vectors In Class"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

```{r include=F}
ex<-F
```

- Create a vector `x` with the values 4,2,3
- Create a vector `m` with the values 5,6,2 
- print `x`
- print `m`

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
x<-c(4,2,3)
m<-c(2,-1,5)
x
m
```

- Use the function `class` to print out info about the vector `x`
- Use the function `class` to print out info about the vector `m` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
class(x)
class(m)
```

- Use the function `str` to print out info about the vector `x`
- Use the function `str` to print out info about the vector `m` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
str(x)
str(m)
```

- Use the function `length` to print out the length of vector `x`
- Use the function `length` to print out the length of vector `m`

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
length(x)
length(m)
```

- Assign `7` to a variable `b` 
- Assign `sum(m*x)+b` to a variable `y` 
- Use `str` to get information about `y` 

```{r include=ex, eval=F}
CODE
```
```{r include=!ex}
b<-7
y<-sum(m*x)+b
y
```

This is exactly like using a regression equation as follows:

$$ y = m_1(x_1) + m_2(x_2) + m_3(x_3) + b $$ 

where `m` is a vector with the slopes:

$$ m = (m_1, m_2, m_3) = (2,-1,5) $$

and `x` is a vector with the x-values: 

$$ x = (x_1, x_2, x_3) = (4,2,3) $$

So that this is calculation is like a prediction using the x-values:

$$ y = 2(4) + -1(2) + 5(3) + 7 = 28 $$ 
