---
title: "Webscraping Laptops"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---
```{r, include=FALSE}
assignment<-TRUE
```

```{r echo=T, results='hide', message=F, warning=F}
if (!require("rvest")) install.packages("rvest")
library("rvest")
```
Read in the page and look for the title the price and the description of each of the items: [e-commerce wepscrape test site](https://webscraper.io/test-sites/e-commerce/allinone/computers/laptops)

```{r}
url<-"https://webscraper.io/test-sites/e-commerce/allinone/computers/laptops"
webpage <- read_html(url)
```

First lets look for the title:

```{r, eval=FALSE, include=assignment}
nodes <- html_nodes(webpage, PUT CODE HERE)
title<- html_text(nodes)
str(title)
```
```{r, eval=!assignment, include=!assignment}
nodes <- html_nodes(webpage, ".title")
title<- html_text(nodes)
str(title)
```

Lets see the first 20 titles in the what we got:

```{r, eval=!assignment}
head(title,20)
```

Next lets look for the price:

```{r, eval=FALSE, include=assignment}
nodes <- html_nodes(webpage, PUT CODE HERE)
price <- html_text(nodes)
price<-gsub("$", "", price, fixed=TRUE)
price <- as.numeric(price)
str(price)
```
```{r, eval=!assignment, include=!assignment}
nodes <- html_nodes(webpage, ".price")
price <- html_text(nodes)
price<-gsub("$", "", price, fixed=TRUE)
price <- as.numeric(price)
str(price)
```

Lets see the first 20 prices in the what we got:

```{r, eval=!assignment}
head(price,20)
```

Next lets look for the description:

```{r, eval=FALSE, include=assignment}
nodes <- html_nodes(webpage, PUT CODE HERE)
description<- html_text(nodes)
str(description)
```
```{r, eval=!assignment, include=!assignment}
nodes <- html_nodes(webpage, ".description")
description<- html_text(nodes)
str(description)
```

Lets see the first few descriptions in the what we got:

```{r, eval=!assignment}
head(description)
```

Next get the number of reviews:

```{r, eval=FALSE, include=assignment}
nodes <- html_nodes(webpage, PUT CODE HERE)
numreviews<- html_text(nodes)
str(numreviews)
```
```{r, eval=!assignment, include=!assignment}
nodes <- html_nodes(webpage, ".ratings .pull-right")
ratings<- html_text(nodes)
str(ratings)
```

Lets see the first few descriptions in the what we got:

```{r, eval=!assignment}
head(ratings)
```

Lets make a data frame with the `title`, `price`,`discription` and `ratings`: 

```{r, eval=FALSE, include=assignment}
df <- PUT CODE HERE
head(df)
```
```{r, eval=!assignment, include=!assignment}
df<- data.frame(title, price, description, ratings) 
head(df)
```

Lets take a look at the histogram of prices:

```{r, eval=!assignment}
hist(price)
```

```{r, eval=!assignment}
range(price)
mean(price)
```

