---
title: "Webscraping Nordstrom Sales Dresses"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r echo=T, results='hide', message=F, warning=F}
options(repr.plot.width=4, repr.plot.height=4)
if (!require("rvest")) install.packages("rvest")
library("rvest")
```

We are going to read in a page at Nordstroms for women's clothing on sale:

```{r}
url <-"https://shop.nordstrom.com/c/sale-womens-clothing"
webpage <- read_html(url)
```

Now we can identify the description of the item:

```{r}
nodes <- html_nodes(webpage, "._28b4r ._2PDR1")
description <- html_text(nodes)
str(description)
```

Lets take a look at the values:

```{r}
print(description)
```

Now we can identify the "Now" current price:

```{r}
nodes <- html_nodes(webpage, "#product-results-view ._35l9g ._3wu-9 , ._18N5Q ._3wu-9")
now <- html_text(nodes)
now <- gsub("$","", now, fixed=TRUE)
now <- as.numeric(now)
str(now)
```

Lets take a look at the values:

```{r}
print(now)
```


Now we identify the "Was" original price:

```{r}
nodes <- html_nodes(webpage, "#product-results-view ._3bi0z ._3wu-9")
was <- html_text(nodes)
was <- gsub("$","", was, fixed=TRUE)
was <- as.numeric(was)
str(was)
```

Lets take a look at the values:

```{r}
print(was)
```

Some of the items prices were given as ranges. So when we converted the strings to numerics they gave us NAs for those. Lets remove those from the description, was and now prices:

```{r}
description <- description[!is.na(was)]
was <- was[!is.na(was)]
now <- now[!is.na(now)] 
```

Lets make a data frame with the `description`, `was`, `now` and `discount` which we will compute: 

```{r}
discount <- round((was-now)/was*100)
df<-data.frame(description,was,now,discount)
print(df)
```

Lets create a new data frame with the discounts sorted:

```{r}
dfnew <- df[order(df$discount),]
rownames(dfnew)<-NULL
print(dfnew)
```

Lets take a look at a histogram of the discounts:

```{r}
#range(discount)
#mean(discount)
#hist(discount)
```

Lets take a look at a histogram of the original prices:

```{r}
#hist(was)
```

Lets take a look at a plot of was vs now prices:

```{r}
#plot(was, now)
```
