---
title: "Webscraping Laptops"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---
```{r, include=FALSE}
assignment<-T
```

```{r echo=T, results='hide', message=F, warning=F}
if (!require("rvest")) install.packages("rvest")
library("rvest")
```
Read in the page and look for the title the price and the description of each of the items: [e-commerce wepscrape test site](https://webscraper.io/test-sites/e-commerce/allinone/computers/laptops)

```{r}
url<-"https://webscraper.io/test-sites/e-commerce/allinone/computers/laptops"
webpage <- read_html(url)
```


- Use the selector gadget selector for the title 
```{r, eval=FALSE, include=assignment}
nodes <- html_nodes(webpage, CODE)
title<- html_text(nodes)
str(title)
```
```{r, eval=!assignment, include=!assignment}
nodes <- html_nodes(webpage, ".title")
title<- html_text(nodes)
str(title)
```

Lets see the first 20 titles in the what we got:

```{r, eval=!assignment}
head(title,20)
```

- Next use the selector gadget selector for the price: 
```{r, eval=FALSE, include=assignment}
nodes <- html_nodes(webpage, CODE)
price <- html_text(nodes)
str(price)
```
```{r, eval=!assignment, include=!assignment}
nodes <- html_nodes(webpage, ".price")
price <- html_text(nodes)
str(price)
```

- Next remove the \$ sign: 
```{r, eval=!assignment}
price<-gsub("$", "", price, fixed=TRUE)
price <- as.numeric(price)
```

Lets see the first 20 prices in the what we got:

```{r, eval=!assignment}
head(price,20)
```


- Next use the selector gadget selector for the description 
```{r, eval=FALSE, include=assignment}
nodes <- html_nodes(webpage, CODE)
description<- html_text(nodes)
str(description)
```
```{r, eval=!assignment, include=!assignment}
nodes <- html_nodes(webpage, ".description")
description<- html_text(nodes)
str(description)
```

Lets see the first few descriptions in the what we got:

```{r, eval=!assignment}
head(description)
```


- Next use the selector gadget selector for the number of reviews 
```{r, eval=FALSE, include=assignment}
nodes <- html_nodes(webpage, CODE)
ratings<- html_text(nodes)
str(ratings)
```
```{r, eval=!assignment, include=!assignment}
nodes <- html_nodes(webpage, ".ratings .pull-right")
ratings<- html_text(nodes)
str(ratings)
```

Lets see the first few descriptions in the what we got:

```{r, eval=!assignment}
head(ratings)
```

- Lets make a data frame with the `title`, `price`,`description` and `ratings`. 
- print out the data frame using the code `knitr::kable(df)`. 
```{r, eval=FALSE, include=assignment}
df <- data.frame(CODE, CODE, CODE, CODE) 
knitr::kable(df)
```
```{r, eval=!assignment, include=!assignment}
df<- data.frame(title, price, description, ratings) 
knitr::kable(df)
```

Lets take a look at the histogram of prices:

```{r, eval=!assignment}
hist(price)
```

```{r, eval=!assignment}
range(price)
mean(price)
```

