---
title: "Webscraping HM sale prices"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

```{r echo=T, results='hide', message=F, warning=F}
if (!require("rvest")) install.packages("rvest")
library("rvest")
```

We are going to read in a page at H&M for sales:

```{r}
# url<-"https://www2.hm.com/en_us/sale/women/tops.html?page-size=2448"
# url<-"https://www2.hm.com/en_us/sale/women/jackets-coats.html?page-size=252"
# url<-"https://www2.hm.com/en_us/sale/women/shirts-blouses.html?page-size=252"
url<-"https://www2.hm.com/en_us/sale/women/dresses.html?page-size=252"
# url<-"https://www2.hm.com/en_us/sale/women/maternity-wear.html?page-size=252"
# url<-"https://www2.hm.com/en_us/sale/women/basics.html?page-size=252"
# url<-"https://www2.hm.com/en_us/sale/women/shoes.html?page-size=252"
# url<-"https://www2.hm.com/en_us/sale/women/jeans.html?page-size=252"
# url<-"https://www2.hm.com/en_us/sale/women/swimwear.html?page-size=252"
# url<-"https://www2.hm.com/en_us/sale/women/accessories.html?page-size=252"
# url<-"https://www2.hm.com/en_us/sale/women/lingerie.html?page-size=252"
# url<-"https://www2.hm.com/en_us/sale/women/view-all.html?page-size=2448"
# url<-"https://www2.hm.com/en_us/sale/women/pants.html?page-size=252"
# url<-"https://www2.hm.com/en_us/sale/women/lingerie.html?page-size=2448"

webpage <- read_html(url)
```

Now we can identify the sale price:

```{r}
nodes <- html_nodes(webpage, ".sale")
sale <- html_text(nodes)
sale <- gsub("$ ","", sale, fixed=TRUE)
sale <- as.numeric(sale)
str(sale,20)
```

Lets take a look at the first few values:

```{r}
head(sale,20)
```

Now we can identify the name of the item:

```{r}
nodes <- html_nodes(webpage, ".item-heading .link")
name <- html_text(nodes)
str(name)
```

Lets take a look at the first few values:

```{r}
head(name,20)
```


Now we identify the regular price:

```{r}
nodes <- html_nodes(webpage, ".regular")
price <- html_text(nodes)
price <- gsub("$","", price, fixed=TRUE)
price <- as.numeric(price)
str(price)
```

Lets take a look at the first few values:

```{r}
head(price,20)
```

Lets make a data frame with the `name`, `sale`, `price` and `discount`: 

```{r}
discount <- round((price-sale)/price*100)
df<-data.frame(name,sale,price, discount)
head(df,20)
tail(df,20)
```

Lets create a new data frame with the discounts sorted:

```{r}
dfnew <- df[order(df$discount),]
names(dfnew)<-NULL
head(dfnew,20)
tail(dfnew,20)
```

Lets take a look at a histogram of the discounts:

```{r}
hist(discount)
```

```{r}
range(discount)
mean(discount)
```

```{r}
plot(price, sale, pch=19)
cor(price, sale)
```
