---
title: "Webscraping Tradesy"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

Install rvest if needed and then load it:

```{r echo=T, results='hide', message=F, warning=F}
options(repr.plot.width=7, repr.plot.height=7)
knitr::opts_chunk$set(fig.width=7, fig.height=7)
if (!require("rvest")) install.packages("rvest")
library("rvest")
```
  
- Now read one of the pages for on-sale at tradesy:
```{r}
url <- "https://www.tradesy.com/on-sale/?page=1&num_per_page=191"
webpage <- read_html(url)
```
  
- Lets try to find the brand from the webpage using selector gadget:
```{r}
nodes <- html_nodes(webpage, ".item-tile__title-link .tdc-bold")
brand <- html_text(nodes)
brand<-trimws(brand)
str(brand)
```
    

- Let's use the `table` function to print out a frequency table (or tally) of the brands.
```{r}
table(brand)
```
    
- Now let's use `barplot` to get a barplot of the frequency table from above. 
```{r}
barplot(table(brand), las=2, horiz=TRUE, main="Brands", cex.names=.5)
```
     
- Now let's use use selector gadget to the the item title 
```{r}
nodes <- html_nodes(webpage, ".item-tile__title-link .tdc-ellipsis-text")
title <- html_text(nodes)
title<-trimws(title)
str(title)
```
     
- Now let's use use selector gadget to the the price 
```{r}
nodes <- html_nodes(webpage, ".item-tile__display-price--sale span:nth-child(1)")
prices<- html_text(nodes)
prices<-gsub(",","",prices)
prices<-sub("$", "", prices, fixed=TRUE)
#orig<-as.numeric(orig)
#price<-gsub("\\s", "", price)
#price<-sub("$", "", price, fixed=TRUE)
#price<-as.numeric(price)
prices<-as.numeric(prices)
str(prices)
```
     
- Now print out the prices and a histogram of prices 
```{r}
prices
```
     
- Now print out a histogram of prices 
```{r}
hist(prices, xlab="prices", breaks=20, main="Prices")
```
