---
title: "Discounts on Poshmark"
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
output:
    ipynbdocument::ipynb_document
---

```{r echo=T, results='hide', message=F, warning=F}
options(repr.plot.width=6, repr.plot.height=6)
knitr::opts_chunk$set(fig.width=6, fig.height=6)
if (!require("rvest")) install.packages("rvest")
library("rvest")
```

Here we will show how to do webscraping with rvest and the chrome extension selector gadget. This technique is borrowed from the great explanation at: [Online Bargin Hunting in R with rvest](https://jef.works/blog/2019/01/12/online-bargain-hunting-in-R-with-rvest/) and is basically a simplified version of that description

So say we want to pull some data from [http://poshmark.com](http://poshmark.com) and compare original prices with the current price, maybe to find excellent bargins. We will look in the category Jackets and Coats-Blazers, and we will just use the data we find on the first page: 

```{r}
url <- 'https://poshmark.com/category/Women-Jackets_&_Coats-Blazers?max_id=1'
webpage <- read_html(url)
```

We just pull the webpage once, then we look for our fields using that pulled page.

Lets look for the title of the item first;

```{r}
nodes<- html_nodes(webpage,'#tiles-con .title')
title <- html_text(nodes)
# This removes some weird non-ascii chars in the title
title <- iconv(title, to="ASCII", sub="")
str(title)
head(title, 10)
```

Next we look for the prices:

```{r}
nodes <- html_nodes(webpage,'div.price')
price <- html_text(nodes)
price<-gsub("\u00A0.*","",price)
price<-gsub("$","",price, fixed=TRUE)
price<-gsub(",","", price, fixed=TRUE)
price<-as.numeric(price)
str(price)
head(price, 10)
```

Now lets look for the original price:

```{r}
nodes <- html_nodes(webpage,'span.original')
original <- html_text(nodes)
original<-gsub("$","",original, fixed=TRUE)
original<-gsub(",","",original, fixed=TRUE)
original<-as.numeric(original)
str(original)
head(original, 10)
```
For our discount analysis we exclude the data where the original is 0:

```{r}
price <- price[original > 0]
title <- title[original > 0]
original <- original[original > 0]
```

Lets compute the discount for each item:

```{r}
discount <- round(100*(original - price)/original)
```

Now lets make a dataframe of the info we have:

```{r}
df <-data.frame(title, price, original, discount)
df[,c("title","original","discount")]
```

Now lets see the distribution of discounts people are offering:

```{r}
discount
#hist(discount)
#mean(discount)
#range(discount)
```

Now lets see the distribution of original prices:

```{r}
original
# hist(original)
# mean(original)
# range(original)
```

Here is a plot of the original vs the offering price:

```{r}
#plot(original,price, pch=19)
#cor(original, price)
```

